---
title: "tidykids Scavenger Hunt"
author: "Awesome Student"
date: '2022-12-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidykids)
library(tidyverse)
```

## `tidykids` scavenger hunt

How many rows are there in the tidykids data set?

```{r}
nrow(tidykids) #23460
# or look in the Environment tab!
```

How many different types are there in the "variable" column?

```{r}
tidykids %>% count(variable) #23 rows
```


What is the average adjusted spending per child on Pell Grants for Florida and California? Report this in $1,000s.

```{r}
tidykids %>%
  filter(state == "Florida" | state == "California") %>%
  filter(variable == "pell") %>%
  group_by(state) %>%
  summarize(mean = mean(inf_adj_perchild)) %>%
  mutate(mean = mean*1000,
         in_dollars = scales::dollar(mean,1))
```


What was the adjusted amount spent per child on Child Tax Credit spending in Hawaii for the year 2010? In $1,000

```{r}
tidykids %>%
  filter(state == "Hawaii",
         variable == "CTC",
         year == 2010) %>%
  pull(inf_adj_perchild)*1000 # $454
```



Stretch Challenges:

What was the percentage change in per child higher ed spending in New York from 2015 to 2016?


```{r}
tidykids %>%
  filter(state == "New York",
         variable == "highered",
         between(year, 2015,2016)) %>%
  select(-c(raw, inf_adj)) %>%
  pivot_wider(names_from=year, values_from = inf_adj_perchild) %>%
  mutate(pct_change = (`2016`-`2015`)/`2015`) # 0.0286 or 2.86%
```



**Bonus**: The adjusted spending for K-12 is based on 2016 dollars. Adjust the spending to 2021 dollars. Then, make a line chart that plots the total original and adjusted spending for all states across all years.

Hint: https://github.com/stevecondylios/priceR 

```{r}
# install.packages("priceR")
library(priceR)

bonus <- tidykids %>%
  filter(variable == "PK12ed") %>%
  mutate(adjusted_2021 = adjust_for_inflation(raw, year, "US", to_date = 2021))

bonus %>%
  group_by(year) %>%
  summarize(raw = sum(raw, na.rm=TRUE),
            adjusted_2021 = sum(adjusted_2021, na.rm=TRUE)) %>%
  pivot_longer(raw:adjusted_2021, names_to = "type", values_to="amount") %>%
  ggplot(aes(x=year, y=amount, color=type, group=type))+
  geom_line()
```

