---
title: "Maps Collaborative Practice"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
    out-width: "100%"
---

```{r setup, include=FALSE}
library(ozmaps) #Austrailaian Shapefiles
library(sf)
library(tidyverse)
```

### 1. Load Oz Maps shapefile/sf object
Just run this chunk to load the `ozmap_states` object from the `ozmaps` package.

```{r load_ozmaps}
ozmap_states_sf <- ozmaps::ozmap_states
```

### 2. Check the class of `ozmap_states_sf`
- If it's an `sf` object, you're good to go.

```{r check_class}

```

### 3. Plot `ozmap_states_sf`
- Assign a different fill color to each state. (e.g.,`fill = as.factor(NAME)`)
- Make the outlines of each state white.
- Also use `geom_sf_label(aes(label = ????))` to label each state.
- Remove the plot legend.
- Apply `theme_void()` to remove the background and axis labels.

```{r plot1_ozmaps}

```

### 4. Remove Australian Capital Territory and Other Territories Features (Rows)
- Copy/paste the code from the previous chunk.
- Use the pipe operator and `slice()` to remove the rows for the Australian Capital Territory and Other Territories.
- Replot the map.

```{r plot2_ozmaps}

```

### 5. Add some more data into the plot
- `oz_pop.csv` is included in your `.zip` file. Load it in below.
- Inspect `oz_pop.csv`. What variables does it include? What class is it? What variable does it have in common with `ozmap_states_sf` (to join on)?
```{r oz_pop}

```

**ANSWERS**:
- Variables:
- Class:
- Variable to join on:

### 6. Joining `oz_states_sf` and `oz_pop`
- Note that we can `left_join()` the two datasets together using the common variable this time. We have a common variable to join on.
- Use `left_join()` to join the two datasets together.

```{r join_oz}

```

### 7. Re-plotting
- Plot the new joined data. 
- Fill each state with the new `Population` variable.
- Make the outlines of each state white.

```{r filled_plot}

```

### 8. Working with oz_pop.csv (again)
- We previously used oz_pop.csv to join with ozmap_states_sf. This let us use the population variable to fill the states/territories..
- But!! oz_pop.csv also has lat/long coordinates for each state/territory capital.
- Use `oz_pop.csv` to plot the capitals for each state/territory.

- To use the lat/long coordinates to plot the capitals, we need to convert the `oz_pop.csv` object to an `sf` object. Let's check to see if it's an `sf` object currently.

```{r check_class2}

```

### 9. Convert oz_pop.csv to an sf object
- Convert the `oz_pop.csv` object to an `sf` object using `st_as_sf()`. Use `crs = 4326` as it's the standard for lat/long coordinates.

```{r oz_pop_to_sf}

```

### 10. Plotting the capitals
- Copy/paste the code from Step #7.
- Add a new `geom_sf()` layer to plot the capitals.

```{r final_plot}

```