---
title: "Week 7 - Working with Text - Teacher"
author: "Amazing Student"
date: '2023-01-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Working Together

<!-- Note to teacher: this section is intended to be done together as a class, having students suggest patterns, fill in blanks, and discuss the code and output -->

Let's load our data, which are assignments and scores from a number of university science classes.

```{r}
data <- read_csv(here::here("Week 7 - Text", "science_course_data.csv"))
```

Let's first take a look at the columns:

```{r}
names(data)
```


And now lets look at the contents of those columns:

```{r}
head(data)
data %>% count(course_section_orig_id)
data %>% count(gradebook_item)
```

We have A LOT of different assignments. But, we can categorize them based on their names. For example, we can likely make the follwing categories: use these recurring keywords to make several categories:

- quiz, test, assessment
- discussion board, discussion, db
- lab
- ?

We will call categorize everything everything else as assignments.

So, how can we do this?

We can use the `stringr` package that gets loaded with the `tidyverse` to work with strings.

Specifically, we are going to use the following two functions right now:

`str_to_lower` - makes text lowercase
`str_detect` - finds text based on a given pattern

```{r}
clean_data <- data %>%
  #create new columns
  mutate(
    # make a "clean" lowercase version of the gradebook items
    gradebook_item_clean = str_to_lower(gradebook_item),
    # detect certain patterns are return a category name
    category = case_when (
      str_detect(gradebook_item_clean, "quiz|test|assessment") ~ "quiz",
      str_detect(gradebook_item_clean, "discussion| db") ~ "discussion",
      str_detect(gradebook_item_clean, "lab") ~ "lab",
      TRUE ~ "assignment"
    ),
     .after="gradebook_item")
```

Let's check our data and see if we need to revise any categories:

```{r}
view(clean_data)
```


What if we wanted to replace all instances of the word "db" with "discussion board"? We can use `str_replace` (which replaces the first occurence of a pattern in a string) or `str_replace_all` (which replaces all occurences within a string):

```{r}
db <- data %>%
  mutate(gradebook_item_clean = str_replace(gradebook_item, 
                                            "db|DB", "Discussion Board"),
         .after="gradebook_item")

view(db)
```

What if we wanted to separate the courses from their section numbers? We can use `separate` from `tidyr`/`tidyverse` for that!

```{r}
course_section <- data %>%
  separate(course_section_orig_id,
           into = c("course", "section"),
           sep = "-",
           extra = "merge")
```


What if we just wanted a simple data frame of course, section, student, and final grade?

```{r}
final_grades <- course_section %>%
  distinct(course, section, user_id, final_grade_cems)
```


# Try It

<!-- Note to teacher: this section is intended to be done individually or with a partner/small group. Students can work on the assignment during class and share the results  -->

1. Recode the dataset to make a new category for non-discussion board writing assignments.

```{r}
clean_data2 <- data %>%
  #create new columns
  mutate(
    # make a "clean" lowercase version of the gradebook items
    gradebook_item_clean = str_to_lower(gradebook_item),
    # detect certain patterns are return a category name
    category = case_when (
      str_detect(gradebook_item_clean, "quiz|test|assessment") ~ "quiz",
      str_detect(gradebook_item_clean, "discussion| db") ~ "discussion",
      str_detect(gradebook_item_clean, "lab") ~ "lab",
      str_detect(gradebook_item_clean, "writing|essay") ~ "writing",
      TRUE ~ "assignment"
    ),
     .after="gradebook_item")
```


2. Recode quizzes, tests, assessments, and exams separatley. Use R to summarize these types of assignments and decide if they should be categorized together or kept separate based on their points possible.

```{r}
clean_data3 <- data %>%
  #create new columns
  mutate(
    # make a "clean" lowercase version of the gradebook items
    gradebook_item_clean = str_to_lower(gradebook_item),
    # detect certain patterns are return a category name
    category = case_when (
      str_detect(gradebook_item_clean, "quiz") ~ "quiz",
      str_detect(gradebook_item_clean, "assessment") ~ "assessment",
      str_detect(gradebook_item_clean, "test") ~ "test",
      str_detect(gradebook_item_clean, "exam") ~ "exam",
      TRUE ~ NA_character_
    ),
     .after="gradebook_item")

clean_data3 %>%
  drop_na(category) %>%
  ggplot(aes(x=points_possible))+
  geom_bar()+
  facet_wrap(~category)

clean_data3 %>%
  drop_na(category) %>%
  group_by(category) %>%
  summarize(min = min(points_possible, na.rm=TRUE),
            median = median(points_possible, na.rm=TRUE),
            avg = mean(points_possible, na.rm=TRUE),
            max = max(points_possible, na.rm=TRUE))


```

Conclusion: Assessments, quizzes, and tests have a similar range of scores, so they can likely be classified togther. "Exams" tend to be different in min and max and so should possibly be kept separate.


3. Make a visualization of the average final score per course. In your visualization, include a title, subtitle, x-axis, y-axis. Include the final score for each course as text in the visualization.

```{r}
final_grades %>%
  group_by(course) %>%
  summarize(avg_final_score = mean(final_grade_cems, na.rm=TRUE)) %>%
  ggplot(aes(x=avg_final_score,
             y=reorder(course, avg_final_score),
             fill=course))+
  geom_col()+
  geom_text(aes(label=paste0(round(avg_final_score),"%")),
            hjust=-.5)+
  scale_x_continuous(limits=c(0,100))+
  labs(title = "Average Final Scores by Course",
       subtitle = "Across all sections",
       y = "Course",
       x = "Average Score")+
  theme_minimal()+
  theme(legend.position = "none",
        axis.title.y = element_text(angle=0, vjust=.5))

```

