---
title: "Assignment 2"
author: "your name"
date: '2022-02-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1: Core R functions

*First, load the tidyverse in the code chunk below*

```{r}

```

*Next, read in the tidykids CSV data and assign it a name*

```{r}

```

*Last, glimpse the data you read in and named*

```{r}

```

## 2: Working with variables (columns)

*Use select to choose the state, variable, year, and inf_adj_perchild variables, and then assign a name to the data that results*

```{r}

```

*Rename the inf_adj_perchild variable to be a bit easier to understand (what the variable represents), again assigning a name to the data that results*

```{r}

```

*Arrange the newly-renamed variable in descending order to see for which state, variable, and year spending was greatest*.

```{r}

```

## 3: Working with rows (observations) and using logical operators

*Filter the data to only include three states of your choosing, assigning a name to the data that results*

```{r}

```

*Group the data by both state and year and then calculate the sum of the spending across variables, assigning a name to the output/data*

```{r}

```

*Finally, create a plot that shows the sum of spending over time by state, replacing my_data with the output/data you named in the step immediately above, and replacing ___ with the names of variables for the x, y, and color aesthetics.* 

```{r}
ggplot(my_data, aes(x = ___, y = ___, color = ___)) +
  geom_point() +
  geom_line()
```

## Bonus: "Compose" a function

*You may have found yourself repeatedly assigning the name to new output. A benefit of using the pipe is that you can "compose" functions together in a series, writing more efficient and easy to read code in the process. Can you compose together all of the data wrangling steps needed to wrangle the data you plotted above into a series?

```{r}

```

## 4: Knit and share your report

When complete, please knit the result to an HTML and submit that for the Week 3 Walkthrough in Canvas. 

Nice job!
