---
title: "Creating and Styling Tables in {gt}"
author: "Amazing Student"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---
<!-- Please edit the knitr options chunk to include message=FALSE and warning=FALSE. -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!--Load in your packages separately. -->
```{r packages}

```

### 1. Reading in Data
- You may use your own data, tidykids data, starwars data, or palmerpenguins data.
```{r read_in_data}

```

### 2. Wrangling Data
```{r wrangle_data}

```

### 3. Creating a Table with {gt}
Requirements for table:

- A title
- A stub
- A source note
- Either Markdown `md()` or HTML `html()` styling
- At least one `tab_style()` argument
```{r create_table}

```

### 4. Adding in Bonus Features
+ 5 pts. for using idea from Tutorial #3
+ 5 pts. for using idea from Tutorial #4
```{r table_with_bonus_features}

```
REQUIRED DOCUMENTATION FOR BONUS!
Which feature did you implement...

- From Tutorial #3: ANSWER HERE
- From Tutorial #4: ANSWER HERE

### 5. Reflection
How did this assignment go? What did you learn? What would you do differently next time? 

ANSWER HERE
