---
title: "Mini Project 1"
author: "Amazing Student"
date: '2022-12-23'
output: html_document
---

# Assignment Introduction

Explore the School Diversity data set and design simple, colorful barcharts.

The data for this mini project comes from the [Washington Post](https://www.washingtonpost.com/graphics/2019/local/school-diversity-data/#methodology). To read more about the source of this data and access a data dictionary, [please click here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-09-24). 

Using this data, you will demonstrate you ability to explore, summarize, and visualize a new data set. In other words, you will apply what we have learned so far to a data set you have not yet seen.

The three sections you must complete are as follows:

- Explore: Demonstrate different ways to explore a data set and become familiar with its contents.

- Summarize: Use various `dplyr` functions to filter, condense, aggregate, and transform the data set into various objects that can be used for visualization

- Visualize: Present simple but useful visualizations that depict interesting information in an aesthetically appealing way.

# Explore

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# load packages here

# read the data
school_diversity <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-24/school_diversity.csv")
```

Demonstrate four different ways to _explore_ the data, focusing on understanding: the columns, the rows, and some characteristics of the data (variable type, summary statistics, counts, etc.).

```{r}

```

# Summarize

Once you are familiar with the data, think of three questions you think the data can answer. Write the questions below and *then* use summarize (and other code) with the data to answer those questions. Note: you will use those summaries in the Visualization section.

Question 1: 

```{r}

```

Question 2: 

```{r}

```

Question 3: 

```{r}

```

# Visualize

Keeping in mind all of the princples of visualization we have learned, all of the `ggplot` functions we have practiced, and all of the visualization code you have seen, develop a visualization that uses the data above. Each visualization should:

1. Present the information clearly
2. Use a custom or non-default color palette
3. Use `theme_minimal` or another theme
4. Have a title, using `ggtitle("title here")`

Visualization 1

```{r}

```

Visualization 2

```{r}

```

Visualization 3

```{r}

```

Please submit your work **as an RMD document** (not an HTML file) in Canvas for Mini Project 1! Good work!

## Grading Criteria

| Criteria                                                            | Yes/No |
|:--------------------------------------------------------------------|:-------|
| The file knits without errors                                       |   []   |
| Functions to explore the data are used correctly                    |   []   |
| The data summarization answers each question the student asks       |   []   |
| The information each visualization depicts is clear                 |   []   |
| Each visualization employees proper color principles                |   []   |
|                                                                     |   []   |
