---
title: "Mini Project 1"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

# Assignment Introduction

Explore the U.S. News and World Report ranking data using the data created by Reiter. 

Please briefly read about the *National University Rankings* Excel data set here:
[https://andyreiter.com/datasets/](https://andyreiter.com/datasets/)

The four sections you must complete are as follows:

1. *Explore*: Demonstrate different ways to explore the data set and become familiar with its contents. We have covered many option in class!

2. *Clean*: Use {dplyr} to clean the data set and prepare it for further analysis.

3. *Summarize*: Use various {dplyr} functions to filter, condense, aggregate, and transform the data set into various objects that can be used for visualization.

4. *Visualize*: Present simple but useful visualizations that depict interesting information in an aesthetically appealing way.

# Explore

Here, load and then explore using non-data visualization means. How many rows and columns are there? What do you notice about the data - what is present and what is missing? Add 3-5 bullet pointed notes below one or more code cells for this step.

# Clean

Using the `dplyr` functions we have learned, clean the data set. Note: There are blank rows and a few rows with strange values in the data. `slice()`, `distinct()`, and `filter()` will be likely useful here. Create at least one code cell below for this step.

# Summarize

Once you are familiar with the data, think of two research questions you think the data can answer. Write the questions below and *then* use `summarize()` (and other code) to begin to explore them. If you get stuck, the practical approach process modeled in Week 4 may help.

*Note 1:* you will build upon the summaries in the Visualization section. 

*Note 2:* your questions do not need to be very rigorous: this is about narrowing your exploration in light of questions you could ask of the data.

**Question 1:** [Write your first research question here.] 

```{r}

```

**Question 2:** [Write your second research question here.]

```{r}

```

# Visualize

Keeping in mind all of the principles of visualization we have learned, all of the `ggplot` functions we have practiced, and all of the visualization code you have seen, develop a visualization that uses the data above. Each visualization should:

1. Present the information clearly
2. Use a custom color palette in at least one visualization. [This resource](https://r-charts.com/colors/) may be useful.
3. Use `theme_minimal` or another theme
4. Have a clear title, and axis labels using `labs()`

**Visualization 1:** (to answer RQ 1)

```{r}

```

**Visualization 2:** (to answer RQ 2)

```{r}

```

## Reflection

Please add a few sentences reflecting on what went well and what was a challenge.

## Render and submit

Be sure to add your name and date. This time, please *change the title of this document in the YAML* to something of your choosing that you think captures the work you have done.

Please submit your work as an HTML file in Canvas for Mini Project 1! Good work!

## Grading Criteria

| Criteria                                                            | Yes/No |
|:--------------------------------------------------------------------|:-------|
| Dataset has been cleaned well                                       |   []   |
| Functions to explore the data are used correctly                    |   []   |
| The data wrangling answers each question the student asks           |   []   |
| The information each visualization depicts is clear                 |   []   |
| Each visualization employees meet aformentioned requirements        |   []   |
| Slack has been used either to ask/answer a question at least once   |   []   |
| One plot has been posted to the plot gallery on Canvas              |   []   |