---
title: 'Assignment 3: College Majors'
author: "Wonderful Student (change to your name!)"
date: '(add the dates)'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load your libraries here
```


```{r}
# Access the data here:
recent_grads <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")

```

## Exploration

Use the functions and techniques we have learned to become familiar with the data set.

Note, for a data "dictionary", visit https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-10-16

```{r}

```

## Summarize the Data

Use the functions and techniques we learned to wrangle and prepare data in the last week for the following task.

Note: Save each answer as an "object" to be used in your visualizations later.

1. Which **major category** has the largest total number of women?

```{r}
women <- recent_grads %>%
  group_by(Major_category) %>%
  summarize(sum = sum(Women))
```

2. Explore the data further using summarize() using groups or variables of your choosing. Please try a different summary statistic than either the sum() or mean() functions we have used so far.

```{r}

```

## Visualize the Data

1. Using your first analysis, develop a **bar chart** that shows which major category has the largest total number of women


```{r}

```

2. Using your own analysis from above, develop one additional bar chart of your choice. Try to go from "tired" to "wired" by using code from the examples provided!

```{r}

```

When complete, please submit this document as an HTML report.

---

## Grading Rubric

| Criteria                                | Yes/No |
|:----------------------------------------|:--------|
| The file knits without errors           |   &check;    |
| Question 1 is answered correctly        |   []   |
| Question 2 is answered correctly        |   []   |
| There is a simple bar chart for Q1      |   []   |
| There is a stacked bar chart for Q2     |   []   |
| There is a third bar chart              |   []   |
