---
title: "Wk9-Collaborative Practice"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
    out-width: "100%"
---

```{r load-tidykids}
library(tidyverse)
```

## STEP 1: Load the data (Already complete)
We are using tidykids data for this exercise.
1. Load the data
2. Create region variable
3. Summarize `inf_adj_perchild` by region and year

```{r load-data}
tidykids <- read_csv("tidykids.csv")

tidykids <- tidykids |>
  select(state, expenditure, year, inf_adj_perchild) |>
  filter(expenditure == "PK12ed") |>
 mutate(region = case_when(
    state %in% c("Maine", "New Hampshire", "Vermont", "Massachusetts", "Rhode Island",
                 "Connecticut", "New York", "New Jersey", "Pennsylvania") ~ "northeast",
    state %in% c("Ohio", "Indiana", "Illinois", "Michigan", "Wisconsin", "Minnesota",
                 "Iowa", "Missouri", "North Dakota", "South Dakota", "Nebraska", "Kansas") ~ "midwest",
    state %in% c("Delaware", "Maryland", "Virginia", "West Virginia", "North Carolina",
                 "South Carolina", "Georgia", "Florida", "Kentucky", "Tennessee",
                 "Alabama", "Mississippi", "Arkansas", "Louisiana", "Oklahoma", "Texas", "District of Columbia") ~ "south",
    state %in% c("Montana", "Idaho", "Wyoming", "Colorado", "New Mexico", "Arizona",
                 "Utah", "Nevada", "California", "Oregon", "Washington", "Hawaii", "Alaska") ~ "west"
  )) |>
  group_by(region, year) |>
  summarize(mean_inf_adj_perchild = mean(inf_adj_perchild, na.rm = TRUE)) |>
  ungroup()
```

## STEP 2: Create initial plot (Already complete)

```{r make-plot}
p <- tidykids |>
  ggplot(aes(x = as.integer(year), y = mean_inf_adj_perchild, color = region)) +
  geom_line(aes(group = region)) +
  labs(title = "U.S. Regional Spending on PK-12 Education by Year",
       y = "Inflation-Adjusted Spending Per Child\n(in Thousands of USD)")
```

## STEP 3: Customize palette & theme (START HERE)
- Use `scale_color_manual` to:
    - Choose a [{MetBrewer}](https://github.com/BlakeRMills/MetBrewer) palette of your choosing to apply
    - Put region names in title case
- Use `theme()` to:
    - Move the legend to the bottom (legend.position)
    - Remove the x axis title (axis.title.x)
    - Make the plot title face bold, size 18, and assign it a color that is complementary to the palette you chose (plot.title)
    - Make x and y axis text bold and size 14 (axis.text)

```{r theme-and-palette}
library(MetBrewer)
# p <- p + 

```

## STEP 4: Fonts!
- Install the {showtext} package and/or load it, depending if you've already initially installed it
- In your console, run `font_families_google()` and pick a font you'd like to use for your plot. You can see them at [Google Fonts](fonts.google.com). Make sure to note the exact name of the font you want to use from the `font_families_google()` output.
- Use `font_add_google` to make the font available for use in your plot
- Run `showtext_auto()` to enable the use of the font
- Change the font in your plot to the one you've selected using `theme(text = element_text(family = "fontname"))`

```{r fonts}
#| fig.showtext = TRUE

#install.packages("showtext")
library(showtext)

font_add_google(name="", family="")

```


## STEP 5: Add annotation
- The amount spent by the northeastern (1st)  and southern (2nd) states in 2016 has been calculated for you. Now, calculate the difference between the two values and store as a third object in your environment
- Use `annotate` to:
    - Add a two-line (`\n` = line break) annotation near the northeastern line in 2016, focusing on the gap between the northeast and the south
    - Use the object name in the statement (i.e., do not hard code the values)
    - Part of this has been done for you. You will need to specify the label text and its x and y coordinates.
    - Assign a color that makes sense with the palette you chose (it's currently set to white)
    
```{r annotation}
ne_2016 <- tidykids |>
  filter(region == "northeast", year == 2016) |>
  pull(mean_inf_adj_perchild) |>
  round(3)

south_2016 <- tidykids |>
  filter(region == "south", year == 2016) |>
  pull(mean_inf_adj_perchild) |>
  round(3)

# Calculate the difference


# Add annotation
p <- p + annotate(
  geom = "text",
  label = FILL ME IN,
  x = FILL ME IN,
  y = FILL ME IN,
  size = 3,
  color = "#FFFFFF",
  hjust = "right"
)

# Note: Because of the way we keep overwriting p, if you make a mistake, you will want to go back and re-run steps 2 and 3 before re-running this code chunk. This is why I typically write plots all in one call, but I wanted to break it up for this exercise.
```

## STEP 6: Output your plot (Already complete)

```{r final-plot}
p
```