---
title: "Assignment 8: Themes and Colors"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

**Please add your name and the date above.**

## Introduction

Fisheries and Aquaculture Department of the Food and Agriculture Organization of the United Nations collects data on fisheries production of countries. [This Wikipedia page](https://en.wikipedia.org/wiki/Fishing_industry_by_country) lists fishery production of countries for 2016. For each country tonnage from capture and aquaculture are listed. Note that countries whose total harvest was less than 100,000 tons are not included in the visualization.

A researcher shared with you the following visualization they created based on these data: https://datasciencebox.org/course-materials/lab-instructions/lab-06/img/fisheries.png

Can you help them improve it? 

## 1. Brainstorming

First, brainstorm how you would improve these visualizations. Write up the changes/decisions you made as bullet points. It’s ok if some of your improvements are aspirational, i.e. you don’t know how to implement it, but you think it’s a good idea.

- **Brainstorm idea 1:** [Please write brainstorm idea #1 here.]
- **Brainstorm idea 2:** [Please write brainstorm idea #2 here.]
- **Brainstorm idea 3:** [Please write brainstorm idea #3 here.]

## 2. Load and explore data

Please install the Data Science in a Box package by running `remotes::install_github("tidyverse/dsbox")` in your console.

```{r}
library(dsbox)
library(tidyverse)

# This is your data from the researcher
fisheries <- dsbox::fisheries
```

Please explore the data in at least two different ways below.

```{r}

```

Write out three exploratory details about the data:

1. **Data detail #1:** [Please write data detail #1 here.]

2. **Data detail #2:** [Please write data detail #2 here.]

3. **Data detail #3:** [Please write data detail #3 here.]

## 3. Data format identification

Is this data in long or wide format? Why?

- **YOUR ANSWER:** [Please write your answer here.]

## 4. Visualize the data

Create a new data visualization for these data that implements what we learned in class. Please be sure to do the following:

- Add a pre-built {ggplot2} theme or theme from another package
- Add 2 theme changes of your choice (title, gridlines, etc.) using `theme()`
- Add a color palette of your choice from an external package (not built into {ggplot2}). Many options are available here: <https://github.com/EmilHvitfeldt/r-color-palettes> or in {paletteer}.
- Move the legend to the bottom

## 5. Reflection
**REFLECTION:** [Please add a sentence or two next reflecting on this assignment. What went well, what was challenging, and what did you learn?]

## 6. Submit

Submit .html file in Canvas. 

**Rubric**

Name is added: 2 points
File knits to an HTML: 4 points
Three brainstorm ideas: 6 points (2 each)
Three exploratory details: 3 points (1 each)
Data format response is correct: 2 points
Visualization + theme/color edits: 15 points

Total: 30 points
