---
title: "Creating Custom Themes in ggplot2"
author: "Names Here Please"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this activity, you will create a custom theme for a plot visualizing spending on children's programs using the `tidykids` dataset. You will modify elements such as titles, background, gridlines, legend, and axis settings in `theme()` to practice creating a custom theme for your plot.

Resources you will/may need:
- [TPTE Identity Toolkit - Colors]
- [Built-in R Color](https://r-charts.com/colors/)
- [`theme()` cheatsheet](https://bookdown.org/alapo/learnr/images/ggplot_elements2.png)
- [`theme()` documentation](https://ggplot2.tidyverse.org/reference/theme)


## Step 1: Load the Required Libraries and Data

You will need to load the `tidykids` dataset and {tidyverse} package to complete this activity. Create a code chunk below and load them both.

## Step 2: Wrangle the Data

Wrangle the data to keep the `year`, `state`, `variable`, and `inf_adj_perchild` columns. Also, create a region variable. I have supplied starter code for the region variable below. Finally, filter `variable` for  PK12ed spending.

```{r wrangling}
# mutate(region = case_when(
#     state %in% c("Maine", "New Hampshire", "Vermont", "Massachusetts", "Rhode Island", 
#                  "Connecticut", "New York", "New Jersey", "Pennsylvania") ~ "Northeast",
#     state %in% c("Ohio", "Indiana", "Illinois", "Michigan", "Wisconsin", "Minnesota",
#                  "Iowa", "Missouri", "North Dakota", "South Dakota", "Nebraska", "Kansas") ~ "Midwest",
#     state %in% c("Delaware", "Maryland", "Virginia", "West Virginia", "North Carolina", 
#                  "South Carolina", "Georgia", "Florida", "Kentucky", "Tennessee", 
#                  "Alabama", "Mississippi", "Arkansas", "Louisiana", "Oklahoma", "Texas", "District of Columbia") ~ "South",
#     state %in% c("Montana", "Idaho", "Wyoming", "Colorado", "New Mexico", "Arizona", 
#                  "Utah", "Nevada", "California", "Oregon", "Washington", "Hawaii", "Alaska") ~ "West"
#   ))
```

## Step 3: Create a Basic Plot

Create a line plot that shows the `inf_adj_perchild` spending over time for all the states. Additionally, facet_wrap by region. Create a code chunk below to do this. Assign the plot to an object called `p`.

## Step 4: Create a Custom Theme

Using the starter code below, begin creating a custom theme to add to your plot. For each additional theme element instruction, copy/paste your code from 4a to 4b, then 4b to 4c, and so on. This will help you build your custom theme step-by-step.

```{r 4a-plot_title}
my_theme <- theme(
  # Increase the size of the plot title to size 18
  # Bold the title
)
```

```{r 4b-axis_labels}
# Copy your completed code from 4a here and then:

# Set the font size for by x and y axis titles to 14.


```

```{r 4c-customize_background}
# Copy your completed code from 4b here and then:

# Change the background color of the plot to light gray.

```
