---
title: "Mini Project 2"
author: "Amazing Student"
date: '2022-12-23'
output: html_document
---

# Assignment Introduction

Many of the data sets we have encountered in this course so far have been curated as part of #TidyTuesday. TidyTuesday is a weekly Twitter-based activity in which users are encouraged to develop creative graphs on newly-posted data by using `ggplot`. This provides users with an opportunity to sharpen their data visualization skills. 

Along with posting the graphics they create, users also typically post the code they used to develop the graphics. This provides an excellent learning opportunity for the online data viz community.

You are going to capitalize on this shared code and improve your own data vizualizaiton skills. Here are the steps for this project:

1. Access [tidytuesday.rocks](https://nsgrantham.shinyapps.io/tidytuesdayrocks/), which is an interface to TidyTuesday posts on Twitter, organized by data set or users.

2. Choose a data set that sounds appealing and begin looking through the Twitter posts to identify an interesting data visualization. This post must have a link to the code, too. (Note 1: check the replies, which sometimes contain the link. Note 2: You **do not need a Twitter account**).

3. Do a data viz tear-down. Copy their code or project. Run their code line-by-line to see how they prepared the data and made their visualization. You can do this for one or more data vizzes from any number of data sets and users.

4. Reflect. Write a short (1-3 paragraphs) reflection piece explaining what you learned from the tear down. This can be about the functions they used. The style they coded in. The colors they applied. The packages they used. The way they laid out their plot. Etc....

5. Apply. Using the provided data set, explore, summarize, and visualize the data. Apply at least one new technique from the tear down **to your visualization** (you can also apply it to the data summarization, but we really want to see it in the visualization.)

Activities 4 and 5 will be completed in this doc below.

Let's goooo!


| Criteria                                                            | Yes/No |
|:--------------------------------------------------------------------|:-------|
| The file knits without errors                                       |   []   |
| A thoughtful reflection is provided                                 |   []   |
| The data summarization answers each question the student asks       |   []   |
| The information each visualization depicts is clear                 |   []   |
| Each visualization employees proper color principles                |   []   |
| Each visualization employees a technique students learned from their data viz tear down.   |   []   |
|                                                                     |   []   |

## Reflection

Link the the TidyTuesday tweet(s) you tore down:

- [title](link)

>Prompt: In 1-3 paragraphs, explain the data visualization techniques (technical and/or aesthetic) you learned from this exercise and how you plan apply it to your own data visualization.
## Application



## Application

This data set comes from the National Center for Educational Statistics, curated on TidyTueday. [See this link for more information and a data dictionary](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-02-02/readme.md). The data is based on Historic Black Colleges and Universities (HBCUs), specifically:

- High school completion and bachelor's degree attainment among persons age 25 and over by race/ethnicity & sex 1910-2016
- Fall enrollment in degree-granting historically Black colleges and universities (HBCU)

Explore the data set, summarize the data, and develop at least 3 visualizations, applying the techniques we have learned in class so far **and** what you learned from your reflections/data viz teardown.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)




hbcu_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-02/hbcu_all.csv')

```


### Explore


### Summarize

Once you are familiar with the data, think of three questions you think the data can answer. Write the questions below and then summarize the data to answer those questions. Note: you will use those summaries in the Visualization section.

Question 1: 

```{r}

```

Question 2: 

```{r}

```

Question 3: 

```{r}

```

### Visualize

Keeping in mind all of the princples of visualization we have learned, all of the `ggplot` functions we have practiced, and all of the visualization code you have seen, and **what you learned from the TidyTuesday data viz tear down**, develop a visualization that uses the data above. Each visualization should:

1. Present the information clearly
2. Use a custom or non-default color palette
3. Use `theme_minimal` or another theme
4. Have a title, using `ggtitle("title here")`
