---
title: "UTK Color Palette"
author: "Colorful Student"
date: '2022-12-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Navigate to [this archive of the UTK color guidelines](https://web.archive.org/web/20210224024222/https://brand.utk.edu/standards/colors/).

## Build a Data Frame of UTK Colors

Use the primary and at least 5 accent colors.

```{r}
utk_data_frame <- tribble(~name,           ~hex,
                          "orange",       "#FF8200",

                          )

utk_data_frame
```
You can preview what these colors look like using the following code:

```{r}
utk_data_frame %>%
  ggplot(aes(y=name, x=1, fill=hex))+
  geom_tile()+
  scale_fill_identity()
```


## Build a Named Vector of UTK Colors

Use the same colors as above to make a named character vector
```{r}
utk_color_vector <- c(
                          "orange"=       "#FF8200",

                          )

utk_color_vector
```



## Using the UTK Color Vector

Our hex values are mapped to color names. How can we use this with data?

Introducing your first function. Run this code:

```{r}
utk_color <- function(...) {
  cols <- c(...)

  if (is.null(cols))
    return (utk_color_vector)

  unname(utk_color_vector[cols])
}
```

Let's try it:

```{r}
utk_color("orange")
utk_color("smokey_gray")
```


Let's apply it to some simple example data:

```{r}
# note this is another way to make a DIY data frame!
example_data <- data.frame(letters=LETTERS[1:5], numbers=sample(5:20, 5))
example_data
```

Map each letter to a UTK color:

```{r}
example_data %>%
  ggplot(aes(x=numbers, y=letters, fill=letters))+
  geom_col()+
  scale_fill_manual(values=c("A" = utk_color("orange"),
                             "B" = 
                             "C" = 
                             "D" = 
                             "E" = 
  ))
```
