---
title: "Maps Collaborative Practice"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
    out-width: "100%"
---

```{r setup, include=FALSE}
library(ozmaps)
library(sf)
library(tidyverse)
```

### 1. Load Oz Maps shapefile/sf object
Just run this chunk to load the `ozmap_states` object from the `ozmaps` package.

```{r load_ozmaps}
ozmap_states_sf <- ozmaps::ozmap_states
```

### 2. Check the class of `ozmap_states_sf`
- If it's an `sf` object, you're good to go.
- If not, convert it to an `sf` object using `st_as_sf()`. Remember! You'll need to know which projection the data is in.

```{r check_class}

```

### 3. Plot `ozmap_states_sf`
- Assign a different fill color to each state.
- Make the outlines of each state white.
- Also use `geom_sf_label(aes(label = ????))` to label each state.
- Remove the plot legend.
- Apply `theme_void()` to remove the background and axis labels.

```{r plot1_ozmaps}

```

### 4. Remove Australian Capital Territory and Other Territories Features (Rows)
- Copy/paste the code from the previous chunk.
- Use the pipe operator and `slice()` to remove the rows for the Australian Capital Territory and Other Territories.
- Replot the map.

```{r plot2_ozmaps}

```

### 5. Add some more data into the plot
- `oz_pop.csv` is included in your `.zip` file. Load it in below.
- Inspect `oz_pop.csv`. What variables does it include? What class is it? What variable does it have in common with `ozmap_states_sf` (to join on)?
```{r oz_pop}

```

**ANSWERS**:
- Variables:
- Class:
- Variable to join on:

### 6. Joining `oz_states_sf` and `oz_pop`
- Note that we can `left_join()` the two datasets together using the common variable this time. We are dealing with one projection (not the AK/HI problem), and have a common variable to join on.
- Use `left_join()` to join the two datasets together.

```{r join_oz}

```

### 7. Final plot
- Plot the new joined data.
- Fill each state with the new `Population` variable.
- Make the outlines of each state white.
- Use `geom_point()` to plot the capital city of each state.

```{r final_plot}

```
