---
title: "Maps Assignment 2"
author: "Awesome Student"
date: '2023-04-23'
output: html_document
---

## 1. Revisiting the tidycensus package

Recall that the tidycensus package, first released in 2017, is an R package designed to facilitate the process of acquiring and working with US Census Bureau population data in the R environment.

Let’s start by getting some illustrative data on the percentage of the population aged 25 and up with a bachelor’s degree or higher from the 2016-2020 ACS, which is stored in the variable `DP02_0068P`.

Please fill out the `get_acs()` function below. If you need help, run `??get_acs()`.

* geography should be tract
* year is 2020
* we're looking for data on Knoxville, TN (what county is it?)
* make sure to specify geometry as `TRUE`

```{r}
knox_bachelors <- get_acs(
  # Your arguments go here
)
```

## 2. Making a base map with leaflet

Create a base leaflet map:

```{r}
library(leaflet)
# see class notes for an example
```

## 3. Defining a color palette

Now, let's define a color palette.

1. For the palette, use your favorite viridis palette: <https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html>
2. Fill out the domain below. The part before the dollar sign should be the data that you are referencing, and the part after should be your quantiative variable.

```{r}
pal <- colorNumeric(
  palette = ______,
  domain = _____$______
)

pal(c(10, 20, 30, 40, 50))
```

## 4. Creating the choropleth

Let's bring it all together.

- The `leaflet()` function initializes the map. Specify the `data` object here.
- `addProviderTiles()` adds a basemap to the map that will be shown beneath the data as a reference. Choose your favorite Provider Tile from here: <https://leaflet-extras.github.io/leaflet-providers/preview/>
- `addPolygons()` adds the tract polygons to the map and styles them.
  - Use the color palette that you create above by specifying the **quantitative variable** that you used to create the palette.
- `addLegend()` then creates a legend for the map, providing critical information about how the colors on the map relate to the data values.

```{r}
leaflet() %>%
  # Add your favorite Provider Tile below
  addProviderTiles(providers$_____) %>%
  addPolygons(data = __________,
              color = ~pal(______),
              weight = 0.5,
              smoothFactor = 0.2,
              fillOpacity = 0.5,
              label = ~ estimate) %>%
  addLegend(
    position = "bottomright",
    pal = pal,
    values = knox_bachelors$estimate,
    title = "% with bachelor's<br/>degree"
  )
```

Take a look at the interactive map of Knox County. Imagine if it were static. What is gained by having an interactive map? What is lost?

ANSWER:

## BONUS

Edit the labels so they are more informative.

## 5. Reflection

Important: After you knit, check the HTML file. 

- Does it appear as you intended?
- Does any output print that is too long?
- Do your name and date appear?

Share any questions you have in Canvas about fine-tuning your .Rmd output.

## 7. Submit

Submit for Assignment 12 in Canvas. 

**Rubric**

- Name is edited: 2 points
- Section 1: 3 points
- Section 2: 3 points
- Section 3: 5 points
- Section 4: 12 points (3 each)
- Section 4 question: 5 points

Total: 30 points