---
subtitle: "Interactive maps with R"
title: "Week 14 - STEM 691"
author: "Joshua Rosenberg and Isabella Velásquez"
format:
  revealjs:
    theme: simple
    transition: fade
    background-transition: fade
    highlight-style: tango
    title-slide-attributes:
      data-background-color: "#4B4B4B"
knitr:
  opts_chunk: 
    fig.align: center
    echo: true
---

## Agenda

- Final projects
- Interactive maps
- Revisit static maps
- Interactive maps with plotly
- Interactive maps with leaflet
- Publishing interactive maps

# Final projects

## Rubric

Given a whole semesters' worth of data viz know-how, how would you assess a data visualization? Which principles and practices would you want to see employed?

We've come up with a starting point: 

<https://bit.ly/stem691-rubric>

## Small group discussion

In small groups in a breakout room, please discuss 3-5 things that you would like to either change or modify. You can make suggestions related to the Major Categories, Expectations, or Point Value. 

**Discuss for five minutes and return to the whole group with a plan for how to share.**

## Process {.scrollable}

For next week, you will need to develop up to three slides. Here are the requirements:

- Presenters should discuss the story of the data, using the visualizations as aids. 
- Your presentation should be no more than 3 slides
- Your presentation should take **3 minutes or fewer**
- Presenters should only speak for 1-2 minutes and take time to answer any questions or interact with the other attendees who appear in their booth.
- This presentation style mimics actual poster presentations that occur at many conferences.

## Process

You can use Google Slides, Powerpoint, Keynote, or another tool. 

To ensure you receive full credit, please upload or share a link to your presentation by 9:00 am on Wednesday, May 1 for the Final Project assignment:

<https://utk.instructure.com/courses/196893/assignments/1779345>

# Interactive maps in R

## Interactivity

- New York Times graphics editor Gregor Aisch noted that only 10 to 15 percent of readers who visit an interactive visualization on their site actually click on anything. 
-  Is it worth the time and effort to make these things? 

. . .

As with most design-related things, it depends on the goals and the audience of your visualization.

## Interactivity

- Immersion

. . .

- Flexibility

. . .

- Zooming, hover-over, pop-ups




## Packages for interactive maps in R

- plotly + ggplot
- leaflet

Other packages include:

- ggigraph + ggplot
- highcharter

# Revisit static maps

## Species Occurrence data

The rgbif package accesses data from the Global Biodiversity Information Facility (GBIF).

```{r}
library(tidyverse)
library(rgbif)
```

## Species Occurrence data

Let's say we want to download data on the Monarch butterfly.

```{r}
dan_ple <- rgbif::occ_data(
  scientificName = 'Danaus plexippus'
)

dan_ple_dat <- dan_ple$data
glimpse(dan_ple_dat)
```

## Download the world map data from rnaturalearth {.smaller}

The package rnaturalearth provides a map of countries of the entire world.

- Use `ne_countries` to pull country data and choose the scale (rnaturalearthhires is necessary for scale = "large")
- Recall the simple feature (sf) standard of data

```{r}
# install.packages("rnaturalearth")
# install.packages("rnaturalearthdata")
library(rnaturalearth)

world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
```

## Making a map {.smaller}

First, let's start with creating a base map of the world using ggplot2's `geom_sf()`.

```{r}
library(ggplot2)
theme_set(theme_minimal())

ggplot(data = world) +
    geom_sf()
```

## Making a map {.smaller}

Reminder that sf geometries are no different than regular geometries, and can be displayed with the same level of control on their attributes:

```{r}
ggplot(data = world) + 
    geom_sf(color = "white", 
            linewidth = 0.1,
            fill = "#0C1337")
```

## Making a map

We can layer the Monarch butterfly data from `dan_ple_dat`:

- Add a new points geometry with `geom_point()`
- Specify the data (since it differs from `world`) with `data`
- Map longitude/latitude to the data with `aes()`

## Making a map {.smaller}

```{r}
ggplot(data = world) + 
    geom_sf(color = "white", 
            linewidth = 0.1,
            fill = "#0C1337") +
  geom_point(data = dan_ple_dat,
             aes(x = decimalLongitude,
                 y = decimalLatitude))
```

## Making a static map

We can layer edit the points according to life stage (`lifeStage`) by specifying `color` in `aes()`.


::: {.callout-note}
Anything not mapped to the data can be put outside of `aes()`
:::

## Making a static map {}

```{r}
ggplot(data = world) + 
    geom_sf(color = "white",
            linewidth = 0.1,
            fill = "#0C1337") +
  geom_point(data = dan_ple_dat,
             aes(x = decimalLongitude,
                 y = decimalLatitude,
                 color = lifeStage),
             size = 0.5)
```

# Adding interactivity

## ggplot2 + plotly

plotly is an R package for creating interactive web-based graphs via the open source JavaScript graphing library `plotly.js`.

```{r}
# install.packages("plotly")
library(plotly)
```

## ggplot2 + plotly

Use the function `ggplotly()` to draw the graph with `plotly.js`.

- Printing the Plotly object will render the chart locally in your web browser or in the RStudio viewer

## ggplot2 + plotly

Wrap your plot in `ggplotly()`:

```{r}
#| eval: false
p <- ggplot(data = world) +
  geom_sf(color = "white",
          linewidth = 0.1,
          fill = "#0C1337") +
  geom_point(
    data = dan_ple_dat,
    aes(x = decimalLongitude,
        y = decimalLatitude,
        color = lifeStage),
    size = 0.5
  )

ggplotly(p)
```

## ggplot2 + plotly

```{r}
#| echo: false
p <- ggplot(data = world) +
  geom_sf(color = "white",
          linewidth = 0.1,
          fill = "#0C1337") +
  geom_point(
    data = dan_ple_dat,
    aes(x = decimalLongitude,
        y = decimalLatitude,
        color = lifeStage),
    size = 0.5
  )

ggplotly(p)
```

# Code along

## Leaftlet

Leaflet is an open-source JavaScript library for interactive maps.

- Simplicity, performance, and usability
- Lots of plugins and documentation

## The leaflet package

Leaflet is a JavaScript library used to build web mapping applications. The leaflet R package makes it easy to create Leaflet maps from R.

```{r}
# install.packages("leaflet")
library(leaflet)
```
 
## The leaflet package: base map

Create a base map with `addTiles()`.

```{r}
leaflet() %>% addTiles()
```

## The leaflet package: tiles {.smaller}

Specify different tile options with `addProviderTiles`

- A list of free tiles is available at <https://leaflet-extras.github.io/leaflet-providers/preview/>

```{r}
leaflet() %>% addProviderTiles(providers$Esri.NatGeoWorldMa)
```

## The leaflet package: zoom

- The different components of the map can be added using the pipe operator `%>%`.

## The leaflet package: zoom
 
```{r}
library(leaflet)
library(dplyr)

leaflet() %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>% 
  setView(lng = -83.9294, lat = 35.9546, zoom = 14)
```

## The leaflet package: markers and tooltips

We can do things like add markers and tooltips.

## The leaflet package: markers and tooltips

```{r}
leaflet() %>%
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>%
  setView(lng = -83.9294, lat = 35.9546, zoom = 14) %>%
  addMarkers(lng = -83.9294, lat = 35.9546,
             popup = "<a href='https://www.utk.edu/'>University of Tennessee, Knoxville</a>")
```

## The leaflet package: bringing in data

```{r}
#| eval: false
leaflet(dan_ple_dat) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 6) %>% 
  addCircles(
    ~ decimalLongitude,
    ~ decimalLatitude,
    popup = dan_ple_dat$scientificName
  ) 
```

## The leaflet package: bringing in data

```{r}
#| echo: false
leaflet(dan_ple_dat) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 6) %>% 
  addCircles(
    ~ decimalLongitude,
    ~ decimalLatitude,
    popup = dan_ple_dat$scientificName
  ) 
```

## The leaflet package: customizing maps

```{r}
#| eval: false
leaflet(dan_ple_dat) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 6) %>% 
  addCircles(
    ~ decimalLongitude,
    ~ decimalLatitude,
    popup = dan_ple_dat$scientificName,
    weight = 9,
    radius = 40,
    color = "#ffa500",
    stroke = TRUE,
    fillOpacity = 0.8
  ) 
```

## The leaflet package: customizing maps

```{r}
#| echo: false
leaflet(dan_ple_dat) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMa) %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 6) %>% 
  addCircles(
    ~ decimalLongitude,
    ~ decimalLatitude,
    popup = dan_ple_dat$scientificName,
    weight = 9,
    radius = 40,
    color = "#ffa500",
    stroke = TRUE,
    fillOpacity = 0.8
  ) 
```

## The leaflet package: adding polygons

```{r}
#| eval: false
leaflet(data = world) %>%
  addTiles() %>%
  addPolygons(
    fillColor = topo.colors(10, alpha = NULL),
    stroke = FALSE,
    label = ~ name
  )
```

## The leaflet package: adding polygons

```{r}
#| echo: false
leaflet(data = world) %>%
  addTiles() %>%
  addPolygons(
    fillColor = topo.colors(10, alpha = NULL),
    stroke = FALSE,
    label = ~ name
  )
```

## The leaflet package: making a choropleth

```{r}
world %>% 
  select(name, gdp_md) %>% 
  head()
```

## The leaflet package: making a choropleth

Specify a color palette and a domain:

```{r}
pal <- colorNumeric("YlOrRd",
                    domain = world$gdp_md)
```

## The leaflet package: making a choropleth

```{r}
#| eval: false
leaflet(data = world) %>%
  addTiles() %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 2) %>% 
  addPolygons(
    fillColor = ~ pal(gdp_md),
    stroke = FALSE
  )
```

## The leaflet package: making a choropleth

```{r}
#| echo: false
leaflet(data = world) %>%
  addTiles() %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 2) %>% 
  addPolygons(
    fillColor = ~ pal(gdp_md),
    stroke = FALSE
  )
```

## The leaflet package: add labels

```{r}
#| eval: false
labels <- paste0(
  "<strong>", world$name, "</strong><br/>GDP: ", world$gdp_md) %>% lapply(htmltools::HTML)

leaflet(data = world) %>%
  addTiles() %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 2) %>% 
  addPolygons(
    fillColor = ~ pal(gdp_md),
    stroke = FALSE,
    label = labels
  )
```

## The leaflet package: add labels

```{r}
#| echo: false
labels <- paste0(
  "<strong>", world$name, "</strong><br/>GDP: ", world$gdp_md) %>% lapply(htmltools::HTML)

leaflet(data = world) %>%
  addTiles() %>%
  setView(lng = -118.259,
          lat = 34.0507666,
          zoom = 2) %>% 
  addPolygons(
    fillColor = ~ pal(gdp_md),
    stroke = FALSE,
    label = labels
  )
```

# Code along
 
# What's next?

Assignment 12 will walk you through creating a Leaflet map.

- Please reach out with any issues!

Final projects!
 