---
title: "Untitled"
author: "Names Here Please"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(rgbif)
library(rnaturalearth)
library(ggplot2)
theme_set(theme_minimal()) # This sets a default ggplot() theme
```

1. We are going to use the `rgbif` package to get data on the occurrence of the domestic cat, *Felis catus*. From the `rgbif` package, use `occ_search()` to get the data on the domestic cat. Assign the result to an object called `cat`. 

```{r cat_rgbif}
cat <- occ_data(scientificName = "Place_Name_Here")
```

2. Use the `$` operator to extract the `data` from the `cat` object and assign it to a new object called `cat_data`. 

```{r cat_data}

```

3. Let's wrangle the `cat_data` to get the number of occurrences of the domestic cat per country. Assign it to `cat_data_sum`. 
```{r cat_data_wrangle}

```

4. Now run the code below to clean up some of the country names so we can cleanly `left_join()` the data (no need to edit the code, just run the block).

```{r clean_country_names}
cat_data_sum <- cat_data |>
  mutate(
    country = case_when(
      country == "Russian Federation" ~ "Russian Federation",
      country == "United Kingdom of Great Britain and Northern Ireland" ~ "United Kingdom",
      country == "Korea, Republic of" ~ "Republic of Korea",
      country == "United States of America" ~ "United States",
      country == "Chinese Taipei" ~ "Taiwan",
      country == "Cabo Verde" ~ "Republic of Cabo Verde",
      country == "Falkland Islands (Malvinas)" ~ "Falkland Islands / Malvinas",
      country == "Iran (Islamic Republic of)" ~ "Iran",
      country == "Türkiye" ~ "Turkey",
      country == "Viet Nam" ~ "Vietnam",
      .default = country
    )
  )
```

5. For the data layer, we'll use the `rnaturalearth` package to get a map of the world. Use `ne_countries()` to get the world map and assign it to an object called `world_sf`. Use a medium scale and ask it to return an sf object.

```{r world_sf}

```

6. Plot the base map of the world using `ggplot2`'s `geom_sf()`. 

```{r world_map}

```

7. Now, let's `left_join()` the `world_sf` and `cat_data_sum` data frames by the `name_long` and `country` columns, respectively. Assign the result to `cat_world`. 

```{r cat_world}

```

8. Now, let's plot `cat_world`. Fill the countries with the number of occurrences of the domestic cat. Make the country borders white and set the linewidth to 0.1.

```{r plotly_country_fill_map}

```

9. Copy and paste the code from the previous chunk. Now, add a `geom_point()` layer to the plot. Use `data = cat_data`, provide the x & y variables in aes, set the size to 0.1 and set the color of the points to a value of your choice. Assign this plot to an object called `p`.

```{r full_plotly_map}

```

10. Finally, let's add interactivity to the plot. Use `ggplotly()` to use plotly.js to render plot `p` made above.

```{r ggplotly_interactive}

```

