---
title: "Week 3 Activity - Summarize + Bar Charts"
author: "Wonderful Student"
date: '2022-12-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidykids)
```

## `Summarize` Activities

> Work together as a class to complete the following code chunks in order to answer the questions.

0. Change the units for inflation adjusted per child spending but multiplying by 1000.

```{r}
______ <- tidykids %>% #assign the output back to tidykids.
  mutate(inf_adj_perchild = inf_adj_perchild*1000)
```

1. What was the mean raw spending per state for PK-12 educational spending?

```{r}
pk12ed_mean_by_state <- tidykids %>%
  ______(variable == "PK12ed") %>%
  group_by(_____) %>%
  summarize(mean_raw = mean(raw))
```

2. What was the median spending on higher ed per person (per child) in the years 2014-2016? What are the top 5 states based on this spending?

```{r}
highered_top_5 <- tidykids %>%
  filter(______ == "highered") %>%
  filter(year %in% c(______,______,______)) %>%
  group_by(state, ______) %>%
  summarize(median = ______(inf_adj_perchild)) %>%
  ungroup() %>%
  group_by(state) %>%
  mutate(max = max(median)) %>%
  ungroup() %>%
  slice(max, n=15)
```

3. What is the proportion of average spending on public health, PK-12, and parks and recreation for FL, CA, TN, and TX?

```{r}
three_categories <- tidykids %>%
  ______(variable %in% c("pubhealth", "PK12ed", "parkrec")) %>%
  filter(state %in% c("______", "______", "______", "______")) %>%
  ______(state, variable) %>%
  ______(mean = round(mean(inf_adj_perchild)), 2) %>%
  mutate(pct = round(prop.table(mean), 2))
```


## Bar Chart Activities

> Explore how to make simple (tired) and slightly more creative (wired) bar charts.

### A Basic Bar Plot 

1. What was the mean raw spending per state for PK-12 educational spending?

#### Tired
*Create a bar chart with mean_raw spending by state.* 

```{r}
pk12ed_mean_by_state %>%
  slice_max(mean_raw, n = 10) %>%
  ggplot(aes(x = ______, y = ______(______, ______))) + #reorder state values by mean_raw
  geom_col()
```

#### Wired

```{r}
pk12ed_mean_by_state %>%
  slice_max(mean, n = 10) %>%
  ______(aes(x = ______, y = reorder(______, ______))) +
  geom_col() +
  scale_x_continuous(labels=scales::dollar_format()) + #add a dollar sign to the x-axis labels
  ylab(NULL) + #specify the y-axis label
  xlab("______") + #specify the x-axis label
  ggtitle("Mean PK-12 Educational Spending",
          subtitle="Top 10 States") +
  theme_minimal()
```

### A Side-by-Side or Dodged Bar Chart 

2. What was the median spending on higher ed per person (per child) in the years 2014-2016? What are the top 5 states based on this spending?

#### Tired

```{r}
highered_top_5 %>%
  ______(aes(x = state, y = median, alpha = year)) + 
  ______(fill = "blue4")

# use alpha for transparencies to distinguish years
```

#### Wired

```{r}
highered_top_5 %>%
  ggplot(aes(x = state, y = median, alpha = ______)) +
  geom_col(position = "dodge", fill = "blue4") + # "dodge" changes the stack to be side-by-side rather than on top of itself
  ylab("Median Spending per Child") +
  xlab("State/Year") +
  ggtitle("Median Spending State - 2014-2016",
          subtitle="Top 5 States") +
  scale_y_continuous(labels = scales::dollar_format()) + 
  guides(alpha = guide_legend(title = "Year")) + #change the legend title
  theme_minimal() +
  theme(legend.position = "top", #changes the position of the legend (can be top, bottom, left, right)
        panel.grid.major.x =  element_blank(), #removes major grid lines 
         panel.grid.minor.x =  element_blank()) #removes minor grid lines 
```

### Stacked Bar Plot

3. What is the proportion of average spending on public health, PK-12, and parks and recreation for FL, CA, TN, and TX?

#### Tired


```{r}
three_categories %>%
  ______(aes(______ = pct, ______ = state, fill = ______)) ______ 
  ______()


```

#### Wired

```{r}
______ %>%
  ggplot(______(x = ______, y = fct_rev(______), ______ = ______)) ______ # fct_rev reverses the states. It can be used on text (characters and factors)
  geom_col() +
  labs(x = NULL,
       y = ______,
       fill = ______) +
  geom_text(aes(label=scales::percent(pct)), # adds percentage to each categorey 
                position=position_stack(vjust=.5)) +
  theme_minimal() +
  scale_x_continuous(labels=scales::percent_format(1))+
  theme(legend.position = "top")+
  scale_fill_manual(values=c("forestgreen", "dodgerblue1", "firebrick1"),
                    guide = guide_legend(reverse = TRUE))
```
