---
title: "Week 3 Activity - Summarize + Bar Charts"
author: "Wonderful Student"
date: '2022-12-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidykids)
```

## `Summarize` Activities

> Work together as a class to complete the following code chunks in order to answer the questions.

1. What was the mean raw spending per state for PK-12 educational spending?

```{r}
pk12ed_mean_by_state <- tidykids %>%
  filter(variable == "PK12ed") %>%
  group_by(state) %>%
  summarize(mean = mean(raw))
```

2. What was the median spending on higher ed per person (per child) in the years 2014-2016? What are the top 5 states based on this spending?

```{r}
highered_top_5 <- tidykids %>%
  filter(variable == "highered") %>%
  filter(year %in% c(2016,2015,2014)) %>%
  group_by(state, year) %>%
  summarize(median = median(inf_adj_perchild)*1000) %>%
  ungroup() %>%
  group_by(state) %>%
  mutate(max = max(median)) %>%
  ungroup() %>%
  slice_max(max, n=15)
```

3. What is the proprotio of average spending on public health, PK-12, and parks and recreation for FL, CA, TN, and TX?

```{r}
three_categories <- tidykids %>%
  filter(variable %in% c("pubhealth", "PK12ed", "parkrec")) %>%
  filter(state %in% c("Florida", "California", "Tennessee", "Texas")) %>%
  group_by(state, variable) %>%
  summarize(mean = round(mean(inf_adj_perchild)*1000)) %>%
  mutate(pct = round(prop.table(mean),2))
```


## Bar Chart Activities

> Explore how to make simple (tired) and slightly more creative (wired) bar charts.

### A Basic Bar Plot {.tabset}

1. What was the mean raw spending per state for PK-12 educational spending?

#### Tired

```{r}
pk12ed_mean_by_state %>%
  slice_max(mean, n=10) %>%
  ggplot(aes(y=reorder(state, mean), 
             x=mean))+
  geom_col()
```

#### Wired

```{r, out.width = "70%"}
pk12ed_mean_by_state %>%
  slice_max(mean, n=10) %>%
  ggplot(aes(y=reorder(state, mean), 
             x=mean))+
  geom_col()+
  scale_x_continuous(labels=scales::dollar_format())+
  ylab(NULL)+
  xlab("Mean")+
  ggtitle("Mean PK-12 Educational Spending",
          subtitle="Top 10 States")+
  theme_minimal()
```

### A Side-by-Side or Dodged Bar Chart {.tabset}

2. What was the median spending on higher ed per person (per child) in the years 2014-2016? What are the top 5 states based on this spending?

#### Tired

```{r}
highered_top_5 %>%
  ggplot(aes(x=state, y=median, alpha=year))+
  geom_col(position = "dodge",
           fill="blue4")
```

#### Wired

```{r}
highered_top_5 %>%
  ggplot(aes(x=state, y=median, alpha=year))+
  geom_col(position = "dodge",
           fill="blue4") +
  ylab("Median Spending per Child")+
  xlab("State/Year") +
  ggtitle("Median Spending State - 2014-2016",
          subtitle="Top 5 States")+
  scale_y_continuous(labels=scales::dollar_format())+
  guides(alpha=guide_legend(title="Year"))+
  theme_minimal()+
  theme(legend.position = "top",
        panel.grid.major.x =  element_blank(),
         panel.grid.minor.x =  element_blank())
```

### Stacked Bar Plot {.tabset}

3. What is the proprotion of average spending on public health, PK-12, and parks and recreation for FL, CA, TN, and TX?

#### Tired


```{r}
three_categories %>%
  ggplot(aes(y=fct_rev(state), x=pct, fill=variable))+
  geom_col()
```

#### Wired

```{r}
three_categories %>%
  ggplot(aes(y=fct_rev(state), x=pct, fill=variable))+
  geom_col()+
  labs(x=NULL,
       y="Percent of Spending",
       fill="Spending Type")+
  geom_text(aes(label=scales::percent(pct)),
                position=position_stack(vjust=.5))+
  theme_minimal()+
  scale_x_continuous(labels=scales::percent_format(1))+
  theme(legend.position = "top")+
  scale_fill_manual(values=c("forestgreen", "dodgerblue1", "firebrick1"),
                    guide = guide_legend(reverse = TRUE))
```
