---
title: "Building a Chloropleth Map Code Along"
author: "Awesome Student"
date: '2023-04-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf) # special feature - spatial data functions
school_diversity <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-24/school_diversity.csv")

```


For this task, we are going to use us school diversity data from the National Center for Education Statistics (NCES) via [#TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-09-24). Visit that link for more information on the data set.

We are going to use this data to make TWO chloropleth maps: a map of diversity by TN school district and a map of average diversity by state.

A chloropleth map = also known as a heatmap, uses color to depict a continuous variable and fills a geographic shape (a county, state, or country) with that color, allowing comparisons across shapes.


# Inspect data

```{r}
names(school_diversity)
view(school_diversity)
```

### Get TN data only

Let's use the latest date available in the data set: 2016-2017.

```{r}
tn_schools <- school_diversity %>%
  filter(ST == "TN",
         SCHOOL_YEAR == "2016-2017") %>%
  janitor::clean_names()
```


### Calculate Diversity

Let's calculate the Simpson's Diversity Index for each LEA (school district). The higher the value, the more diverse the group is. It is derived from the US Census calculations. See http://dpanther2.fiu.edu/itis/diversityIndex.html

```{r}
diversity <- function(x) {
  
  pop <- sum(x, na.rm=TRUE)
  proportions <- x/pop
  d = 1-sum(proportions^2)
  return(d)
}


tn_diversity <- tn_schools %>%
  # make a wide table
  pivot_longer(aian:multi,
               names_to = "group",
               values_to="n") %>%
  # estimate population numbers from total and proporitions
  mutate(n = (n/100)*total) %>%
  group_by(leaid, lea_name) %>%
  summarize(diversity_index = diversity(n))
```

# Get TN school districts

We can access TN school districts via its shapefiles - a file format that stores geographic location information.

Visit https://www.census.gov/cgi-bin/geo/shapefiles/index.php and download the Unified School District shapefiles for Tennessee for the 2016 school year. Extract the files into a folder called "shapefiles". There are numerous files. Please extract them all.

```{r}
# read in the shapefile data
tnsf <- read_sf("shapefiles/tl_2016_47_unsd.shp") %>%
  janitor::clean_names()

# Note, you may also be able to use the leaidr  package to get similar files
# https://rfortherestofus.com/resource/leaidr/
# devtools::install_github("ivelasq/leaidr")
# library(leaidr)
# tnlea_map <- lea_get("tn")
```

### Join Data and Shapefiles

Connect the diversity data to the geographic data.

```{r}
names(tn_diversity)
names(tnsf)

tn_map_data <- tnsf %>%
  left_join(tn_diversity, by = c("geoid" = "leaid"))
```


# Make a Map

Use `geom_sf` to plot the geographic data and `coord_sf` to ensure the correct map proporitions

```{r}
ggplot() + 
  geom_sf(data = map_data, 
          color = "#616161", # line color
          aes(fill=diversity_index)) +
  coord_sf()+
  scale_fill_viridis_c(direction=-1,# darker = more diversity
                       labels=scales::percent_format(),
                       name="Diversity\nIndex")+ 
  ggtitle("Tennessee School District Diversity - 2016-17")+
  theme_minimal()+
  theme(axis.text = element_blank())
```


# Make it Interactive

We can use the `plotly` package to turn this into a simple interactive map.

```{r}
tn_diversity_map <- ggplot() + 
  geom_sf(data = map_data, 
          color = "#616161", # line color
          aes(fill=diversity_index,
              # This will be used in the tooltip of the plotly interactive map
              text=paste0(str_to_title(lea_name), "\n",
                          scales::percent(diversity_index,2)
                          ))) +
  coord_sf()+
     scale_fill_viridis_c(direction=-1,# darker = more diversity
                       labels=scales::percent_format(),
                       name="Diversity\nIndex")+ 
  ggtitle("Tennessee School District Diversity - 2016-17")+
  theme_minimal()+
  theme(axis.text = element_blank())

# install.packages("plotly")
library(plotly)
tn_diversity_map %>%
  ggplotly(tooltip="text")
```

# Let's Make an Interactive Map of the US

This map will use the highcharter package to make it interactive

```{r}
library(highcharter)

us_diversity <- school_diversity %>%
  janitor::clean_names() %>%
  filter(school_year == "2016-2017") %>%
   pivot_longer(aian:multi,
               names_to = "group",
               values_to="n") %>%
  # estimate population numbers from total and proporitions
  mutate(n = (n/100)*total) %>%
  group_by(st, lea_name) %>%
  summarize(diversity_index = diversity(n)) %>%
  group_by(st) %>%
  summarize(avg_diversity = mean(diversity_index, na.rm=TRUE)*100)
```


```{r}
mapdata <- get_data_from_map(download_map_data("countries/us/us-all")) %>%
    rename(state = `postal-code`) #this is the state abbreviation

hcmap("countries/us/us-all", data = us_diversity,
      name = "Average Diversity", value = "avg_diversity", 
      joinBy = c("postal-code", "st"),
      borderColor = "transparent") %>%
  hc_colorAxis(dataClasses = color_classes(c(seq(0, 100, by = 10)))) %>% 
  hc_legend(layout = "vertical", align = "right",
            floating = TRUE, valueDecimals = 0, valueSuffix = "%") %>%
  hc_tooltip(valueDecimals = 2,
             valueSuffix = "%") %>%
  hc_title(text = "Diversity in American School Districts (2017)",
           margin = -5,
           style = list(fontSize = "18pt", useHTML = TRUE)) %>%
  hc_subtitle(text = "The following chart represents the average school district diversity of each state.")
```
