---
title: "Creating Custom Themes in ggplot2"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

## Introduction

In this activity, you will create a custom theme for a plot visualizing spending on children's programs using the `tidykids` dataset. You will modify elements such as titles, background, gridlines, legend, and axis settings in `theme()` to practice creating a custom theme for your plot.

Resources you will/may need:

- [MetBrewer documentation](https://github.com/BlakeRMills/MetBrewer)
- [Built-in R Color](https://r-charts.com/colors/)
- [`theme()` cheatsheet](https://bookdown.org/alapo/learnr/images/ggplot_elements2.png)
- [`theme()` documentation](https://ggplot2.tidyverse.org/reference/theme)


## Step 1: Load the Required Libraries and Data

You will need to load the `tidykids` dataset and {tidyverse} package to complete this activity. Create a code chunk below and load them both.

## Step 2: Wrangle the Data

Wrangle the data to keep the `year`, `state`, `expenditure`, and `inf_adj_perchild` columns. Also, create a region variable. I have supplied starter code for the region variable below. Finally, filter `variable` for  PK12ed spending.

```{r wrangling}
# mutate(region = case_when(
#     state %in% c("Maine", "New Hampshire", "Vermont", "Massachusetts", "Rhode Island", 
#                  "Connecticut", "New York", "New Jersey", "Pennsylvania") ~ "Northeast",
#     state %in% c("Ohio", "Indiana", "Illinois", "Michigan", "Wisconsin", "Minnesota",
#                  "Iowa", "Missouri", "North Dakota", "South Dakota", "Nebraska", "Kansas") ~ "Midwest",
#     state %in% c("Delaware", "Maryland", "Virginia", "West Virginia", "North Carolina", 
#                  "South Carolina", "Georgia", "Florida", "Kentucky", "Tennessee", 
#                  "Alabama", "Mississippi", "Arkansas", "Louisiana", "Oklahoma", "Texas", "District of Columbia") ~ "South",
#     state %in% c("Montana", "Idaho", "Wyoming", "Colorado", "New Mexico", "Arizona", 
#                  "Utah", "Nevada", "California", "Oregon", "Washington", "Hawaii", "Alaska") ~ "West"
#   ))
```

## Step 3: Create a Basic Plot

Create a line plot that shows the `inf_adj_perchild` spending over time for all the states. Additionally, facet_wrap by region. In your `facet_wrap()` call, add `scales = "free_x"` or `scales = "free_y"` depending on which axis your states are on (make the state axis free). Add plot and axis labels. Create a code chunk below to do this. Assign the plot to an object called `p`.

## Step 4: Use a Theme Package

Use a theme package of your choosing (e.g., MetBrewer or something from Paletteer) to add a theme to your plot. Create a code chunk below and assign the plot to `p_theme`.

## Step 5: Customize the Theme

Using the starter code below, let's make some edits to the theme you chose (i.e., you'll override some portions of the theme you chose in step 4). To do this, we'll begin creating a custom theme to add to your plot. For each additional theme element instruction, copy/paste your code from 5a to 5b, then 5b to 5c, and so on. This will help you build your custom theme step-by-step.

```{r 5a-plot_title}
my_theme <- theme(
  # Increase the size of the plot title to size 18
  # Bold the title
)
```

```{r 5b-axis_labels}
# Copy your completed code from 5a here and then:

# Set the font size for by x and y axis titles to 14. Change the color for each to smokey gray (#4B4B4B).


```

```{r 5c-customize_background}
# Copy your completed code from 5b here and then:

# Change the background color of the plot to a light gray. Add a black border around each panel.

```

```{r 5d-gridlines}
# Copy your completed code from 5c here and then:

# Remove the minor gridlines from the plot. Change the color of the major gridlines to white.

```

```{r 5e-legend}
# Copy your completed code from 5d here and then:

# Change the legend position to the bottom of the plot.
```

## Step 6: Finalize the Plot

Let's combine everything into a final plot. This may not look fantastic, depending on the combination of the theme package you chose plus the specific asks in part 5, but the point is that you were able to do both! Create a code chunk below and assign the plot to an object called `p_final`. To do this, you will want to combine either `p + custom_theme_package + 5e` or `p_theme + 5e`. Do this in a code chunk below. Make sure you call `p_final` at the end of the chunk to display the plot.