---
title: "Collaborative Practice: Comparing Amounts"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

1. Load {tidyverse} in the code cell below.
```{r packages}

```

2. Read in the `gapminder.csv` file into R. Assign the resulting data frame to a new object called `gapminder`.
```{r data}

```

3. Filter the data set to include only observations from the year 2007. Assign this subset to a new object called `gapminder_2007`.

```{r 2007-filter}

```

4. Using `gapminder_2007`, calculate the average life expectancy for each continent. Then, create a dot plot to display these averages, with one point per continent. Use `labs()` to give your plot a title and label the axes. Reorder the dots/continents from lowest to highest life expectancy.

Hints: 
- First, use `group_by()` and `summarize()` to calculate the averages.
- Remember to `ungroup()` after summarizing to avoid issues with subsequent operations.
- Use `geom_point()` to create the dot plot.
- `fct_reorder()` from the {forcats} package can be used along with `mutate()` to reorder the continents based on the average life expectancy. Do this before the `ggplot()` call.

```{r life-expectancy-dot-plot}

```

5. First, categorize countries into "High GDP" or "Low GDP" groups based on the median GDP per capita for 2007.

Hint:
 - Use `mutate()` and `case_when()` to create a new variable called `gdp_category` that labels countries as "High GDP" if their GDP per capita is equivalent to or above the median, and "Low GDP" if below.
 
```{r gdp-category-variable-creation}

```

6. Using the `gapminder_2007` dataset with your new `gdp_category` variable, create a dot plot that shows the average life expectancy for countries in the "High GDP" and "Low GDP" categories. Note that the plot should have one point per gdp category (i.e., two points total). Please use `coord_flip()` to flip the plot, placing GDP categories on the left-hand side.

Hint:
- Group by `gdp_category` and calculate the average life expectancy for each group.
- Ungroup after summarizing to avoid issues with subsequent operations.

```{r dot-plot-gdp-categories}

```


7. Using the full `gapminder` dataset, create a bar plot (`geom_col()`) comparing the average GDP per capita across continents for each year. Use either faceting or dodging to compare the GDPs side by side for each year.

Hints:
- Group by `continent` and `year` to calculate the average GDP per capita.
- Experiment with faceting and dodging to see which you like better.

```{r gdp-bar-plot}

```


8. Choose only ONE continent. Create a heatmap using `geom_tile()` to show the population of each country over time. The x-axis should represent years, the y-axis should represent countries, and the fill should represent population size.

```{r population-heatmap}

```


9. Use `ggsave()` to save your heatmap from exercise 6 as a .png file.

```{r ggsave-heatmap}
ggsave(plot = last_plot(), filename = "heatmap.jpg", height = 6, width = 10)
``` 
 