---
title: "My First Data Visualization"
author: "XXX"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE
)
```

First, please replace XXX (in the author field in the front matter) with your name!

## Install Packages

Packages perform different jobs in R. Packages allow you to use specific functions in R. They allow R to do new things.

Before we can use a package, we need to install it. We can install it using `install.packages("package_name")`. We only need to run this the first time we install a package.

For our first visualization, we are going to install:

- `tidyverse` - used for loading and wrangling data
- `here` - used to easily access files within a project

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# NOTE: skip this step if you already have these installed. You will need to uncomment the code below to install the packages. (i.e., remove the # symbol)
# install.packages("tidyverse")
# install.packages("here")
```

## Load Packages

Here, please load the tidyverse and here packages (using the library function).

```{r}

```


## Load Data

The data is located in the `week-2` folder and is called `gapminder.csv`. We will use the `read_csv` function from the `tidyverse` package to load the data.

Please replace XXX with the name gapminder_data, as we will be using that in the next code chunk

```{r}
XXX <- read_csv(here("week-2", "gapminder.csv"))
```

## Prepare Data

Below, edit `filter()` to only select the year 2007. After modifying and running this block, make sure gapminder_cleaned only contains data from 2007.

```{r}
gapminder_cleaned <- gapminder_data %>% 
  # select only the year 2007
  filter(XXXXX) %>%
  # change columns
  mutate(
    # Place any country in Oceania in Asia
    continent = ifelse(continent == "Oceania", "Asia", as.character(continent)),
    # Create the factor order for the continents
    continent = factor(continent, levels=c("Asia", "Americas", "Europe", "Africa"))
  ) 
```

## Build a Visualization

*Note:* Visualization based on example from https://ggplot2tutor.com/tutorials/gapminder

Run this block. It will create a visualization of life expectancy and income in 2007.

```{r fig.height = 6, fig.width=10}
ggplot(data = gapminder_cleaned, 
       aes(x = gdpPercap, 
           y = lifeExp)) +
      annotate("text", x = 4000, y = 45, hjust = 0.5,
           size = 85, color = "grey80",
           label = "2007", alpha = .3)+
  geom_point(aes(size = pop, fill = continent),
             shape = 21,
             color = "black")+
  guides(size = "none",
         fill = guide_legend(override.aes = list(size = 5)))+
  scale_fill_manual(values = c("Asia" = "#c15dcb",
                                "Americas" = "#057575",
                                "Africa" = "#ff7500" ,
                                "Europe" = "#1E90FF"),
                     name=NULL) +
  scale_x_log10(breaks = c(0500, 1000, 2000, 4000,
                           8000, 16000, 32000, 64000))+
  scale_y_continuous(breaks = seq(0, 120, by = 10))+
  scale_size_continuous(range = c(1, 30))+
  annotate("curve", x = 2500, xend = 2014, y = 39, yend = 46.9, 
           color = "#606F7B", linetype = 2, size = .2,  curvature = 0.5)+
  annotate("text", x = 2300, y = 30, hjust = 0,
           size = 3.5,
           label = paste0("Nigeria had a life expectancy of\n",
                          "46.9 years and an annual income of",
                          "\n$2014 per year per person in 2007"))+
    labs(
    x = "Income",
    y = "Life expectancy",
    title = "Life Expectancy and Income in 2007",
    subtitle = paste0("In the following visualization you can see the relationship between income and life expectancy among all countries in 2007.",
                      "\nAfrican countries are still lagging behind in terms of general life expectancy. The European and American countries",
                      "\nare the healthiest and richest countries in the world."),
    caption = "per person (GDP/capita, PPP$ inflation-adjusted)"
  ) +
  theme(
    panel.background =element_rect(fill="white", color="white"), 
    plot.margin = unit(rep(1, 4), "cm"),
    plot.title = element_text(size=14, face="bold"),
    plot.caption = element_text(size=8, color="grey50"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = 0.2, 
                                    color = "#e5e5e5"),
    axis.title.y = element_text(margin = margin(r = 15), 
                                size = 11),
    axis.title.x = element_text(margin = margin(t = 15), 
                                size = 11),
    axis.line = element_line(color = "#999999", 
                             size = 0.2),
    legend.position = "top"
  ) +
  coord_cartesian(ylim = c(0, 100))
```

After successfully buliding the plot, change **one thing** in the code and re-run it. It could be something like changing a color, or clarifying the title or axis label(s).

## Save the plot

```{r}
ggsave(plot=last_plot(), filename = here("week-2", "gapminder.jpg"), height = 6, width=10)
```

Make sure you can view it in the file pane --> try double-clicking it.

## Rubric

|                     | Points Possible | Points Earned |
|---------------------|-----------------|---------------|
| File knits to HTML  | 10              |               |
| All edits correct.  | 10              |               |
| .html is submitted. | 5               |               |
| .jpg is submitted   | 5               |               |


## Knit and Submit

Complete the following steps to knit and publish your work:

1.  First, double-check check that the the name of the `author:` in the [YAML header](https://bookdown.org/yihui/rmarkdown-cookbook/rmarkdown-anatomy.html#yaml-metadata) at the very top of this document displays your name. The YAML header controls the style and feel for knitted document but doesn't actually display in the final output.

2.  Next, click the knit button in the toolbar above to "knit" your R Markdown document to a [HTML](https://bookdown.org/yihui/rmarkdown/html-document.html) file that will be saved in your R Project folder. You should see a formatted webpage appear in your Viewer tab in the lower right pan or in a new browser window. Let's me know if you run into any issues with knitting! 

3. Upload the HTML file that is now present in the same folder as this R Markdown file to Canvas to receive credit! Also, please upload the JPG file to receive full credit (so, you will upload TWO files for this assignment).
