---
title: "Assignment 5"
name: "xx"
output: html_document
date: "xx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment is also fairly open-ended. Please consult the slides, particularly attending to the following considerations:

1. Make sure you have *amounts* and not *distributions*
2. Make the labels readable
3. Order bars in a logical manner
4. Stack, dodge, or facet, when appropriate

## 1. Get set up

First, change the name and date in the YAML.  Then read the tidykids data into R, and assign a name to the data in the code chunk below.

```{r}

```

## 2. Explore the data

Last week in step 2, you were also asked to explore the tidykids data. It's a fine practice to copy/reuse code, so you can copy and paste your code from the last assignment into the code chunk below. Then, make one addition to what you did to explore the data last week.

```{r}

```

## 3. Graph 1: An effective visualization of amounts

Please complete an effective visualization of amounts using the tidykids data with a bar (i.e., column) chart, keeping in mind the afrementioned considerations. Then, add 1-2 sentences interpreting your visualization.  Like last week, please let the open-endedness be fun, not a burden. 

## 4. Graph 2: Modifying Graph 1

If you haven't yet, please *set* the color of your bars using its hex code or name (run `colors()` for names, and use any number of web-based tools to find the hex code, e.g.: https://htmlcolorcodes.com/color-picker/)

## 5. Graph 3: Create a stacked, dodged, or faceted bar chart

Please create a stacked, dodged, or faceted bar chart, again keeping in mind the (other) considerations. You may find the recording and slides (both uploaded to Canvas) helpful. Please add 1-2 sentences interpreting what you've found. Please note, you may need to manipulate the data using various dplyr functions to successfully complete this step. It may be a challenge, but for this and the next graph, perfection is not the goal! Getting a feel for when and how to create this kinds of plots is, so try to create something sensible as a first attempt at doing so.

```{r}

```

## 6. Graph 4: Set a theme 

Using any of the graphs you have created so far, use the pre-installed themes(https://ggplot2.tidyverse.org/reference/ggtheme.html) or install ggthemes (or another package that provides themes, if you wish) and add the theme to your plot.

```{r}

```

## 7. Graph 5: - Histogram!

Histograms were challenging last week. Try again this week using the starwars data set (it is built in and can be accessed by typing `starwars`). Note that you only set one aesthetic (either `x` or `y`) and then use `geom_histogram()`. Adjusting the binwidth is often a good idea!

```{r}

```

## 8. Bonus: Create a different stacked, dodged, or faceted bar chart

Optionally and to push yourself, either change the graph you created for Graph 3 - or create a new graph - using a different type of bar chart than then one you have created. For example, if you created a stacked bar chart, create either a dodged or faceted bar chart. Again, perfection is absolutely not the goal.

## 9. Bonus: Create a bar chart with your data

Again, optionally, read in and create a bar chart with your data (maybe you have some from a project or a paper you're working on? Otherwise, use tidykids or starwars). Add a sentence or two interpreting what you found. 

## 10. Reflection

When complete, please knit the result to an HTML (be sure to add your name at the top!) and submit that for Assignment 5 in Canvas.  Please note, you are only submitting the HTML output for this assignment.  

Please add a sentence or two next reflecting on this assignment. What went well, what was challenging, and what do you want to dive deeper into?

**Rubric**

Name is added: 2 points
File knits to an HTML: 8 points
Code chunks have appropriate output: 15 points
Interpretations and reflection are added: 5 points
Bonus: 5 points
Total: 30 points