---
title: "Untitled"
output: html_document
date: "2024-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first thing I will need to do after data cleaning will be to determine factor loadings on my
latent variables (mindset behavior and gritty behavior). I have access to data that will allow me
to build one additional latent variable, college readiness, but I am not sure it will fit with the
questions I am really interested in exploring at this point. Mindset behavior will be built from the
cumulative score (positive or negative) of the midterm to final grade relationship (do the grades
increase or decrease from the midterm to the final grade?), which will be called TotalTrend, the
mean number of semesters that pass between the time a student fails a course and the semester
they retake the course, which will be called Retakes, and the percentage of courses passed, which
will be called PassPercent. Gritty behavior will be a newly built latent variable for this study,
which will consist of the number of semesters a student pursues their major, the number of
semesters in a row a student takes coursework in the same subject area, and persistence to
graduation.

```{r}
library(tidyverse)
# 
```