---
title: "Assignment 6"
output: html_document
date: "2023-03-19"
---

## All together now

### Loading tidyverse and ggrepel (may need to install the first time using install.packages)

```{r}

```

### Viewing the built-in midwest dataset

```{r}
midwest
```

### Selecting two variables - poptotal and percbelowpoverty - as well as county and state

```{r}

```

### Doing some text wrangling with stringr

**https://stringr.tidyverse.org/**

```{r}

```

### Plotting poptotal by percbelowpoverty with labels: geom_text()

```{r}

```

### Plotting poptotal by percbelowpoverty with labels: geom_text_repel()

```{r}

```

### Plotting poptotal by percbelowpoverty with labels: geom_text_repel() and labs()

```{r}

```

## Independently

### Viewing the built-in us_rent_income dataset (hint: type the name in the box below)

```{r}

```

### Remove the moe and GEOID variables from the data set (hint: use select and the minus symbol to remove a column) and then save the results back to us_rent_income

```{r}

```

### Pivot the data set to be in "wide" format using pivot_wider, replacing xx below with variable and yy with estimate, saving the results back to us_rent_income after

```{r}
us_rent_income <- us_rent_income %>% 
  pivot_wider(names_from = variable, values_from = estimate)
```

### Create a new variable, rent_yearly, that is equal to rent multiplied by 12

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text()

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text_repel()

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text_repel() and labs() (i.e., change the title, subtitle, caption, and x and y axis labels)

```{r}

```

### Bonus: Use mutate() to create a new variable, prop_of_income, that represents the proportion of income made up by rent; then, make the state NAME equal to NA if this proportion is less than .50 and use geom_text() to visualize the result (which should only include text for states with a proportion greater than .50).

```{r}

```

## Done!

Please knit to HTML and submit for Assignment 4