---
title: "Assignment 6"
output: html_document
author: "Joshua R."
date: "2023-03-19"
---

## All together now

### Loading tidyverse and ggrepel (may need to install the first time using install.packages)

```{r}
library(tidyverse)
# install.packages("ggrepel")
library(ggrepel)
```

### Viewing the built-in midwest dataset

```{r}
midwest
```

### Selecting two variables - poptotal and percbelowpoverty - as well as county and state

```{r}
midwest <- midwest %>% 
  select(poptotal, percbelowpoverty, county, state)

midwest
```

### Doing some text wrangling with stringr

**https://stringr.tidyverse.org/**

```{r}
# str_to_sentence("ocala")
# str_to_title("ocala wayne")

midwest <- midwest %>% 
  mutate(county = str_to_lower(county),
         county = tools::toTitleCase(county),
         county = str_c(county, ", ", state))

midwest <- midwest %>% 
  select(-state)

midwest
```

### Plotting poptotal by percbelowpoverty with labels: geom_text()

```{r}
midwest %>% 
  ggplot(aes(x = poptotal, y = percbelowpoverty, label = county)) +
  geom_point() +
  geom_text()
```

### Plotting poptotal by percbelowpoverty with labels: geom_text_repel()

```{r}
midwest %>% 
  ggplot(aes(x = poptotal, y = percbelowpoverty, label = county)) +
  geom_point() +
  geom_text_repel(max.overlaps = 20)
```

### Plotting poptotal by percbelowpoverty with labels: geom_text_repel() and labs()

```{r}
options(scipen = 10000000)

midwest %>% 
  ggplot(aes(x = poptotal, y = percbelowpoverty, label = county)) +
  geom_point() +
  geom_text_repel(max.overlaps = 20) +
  labs(title = "Poverty Rate by Population",
       subtitle = "In Five Midwest States",
       x = "Population",
       y = "Percentage Below Poverty",
       caption = "Most counties are small and with relatively low poverty rates") +
  theme_minimal()
```

## Independently

### Viewing the built-in us_rent_income dataset (hint: type the name in the box below)

```{r}

```

### Remove the moe and GEOID variables from the data set (hint: use select and the minus symbol to remove a column) and then save the results back to us_rent_income

```{r}

```

### Pivot the data set to be in "wide" format using pivot_wider, replacing xx below with variable and yy with estimate, saving the results back to us_rent_income after

```{r}
us_rent_income <- us_rent_income %>% 
  pivot_wider(names_from = variable, values_from = estimate)
```

### Create a new variable, rent_yearly, that is equal to rent multiplied by 12

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text()

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text_repel()

```{r}

```

### Create a scatterplot with x representing income and y representing rent; label the points using geom_text_repel() and labs() (i.e., change the title, subtitle, caption, and x and y axis labels)

```{r}

```

### Bonus: Use mutate() to create a new variable, prop_of_income, that represents the proportion of income made up by rent; then, make the state NAME equal to NA if this proportion is less than .50 and use geom_text() to visualize the result (which should only include text for states with a proportion greater than .50).

```{r}

```

## Done!

Please knit to HTML and submit for Assignment 4