---
title: "Week 2 `tidykids` Walk Through"
author: ""
date: '2022-12-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
remotes::install_github("jrosen48/tidykids")
```


How can we load the `tidykids` package?

```{r}
library(tidykids)
```



How can we view the data in R Studio as a spreadsheet?

```{r}
view(tidykids)
```


How can we view the first 10 rows of tidykids?

```{r}
head(tidykids, n=10)
```

How about the last 5 rows?

```{r}
tail(tidykids, n=10)
```


How can we see the structure of the data?

```{r}
str(tidykids)
```

How can we list the column names?

```{r}
names(tidykids)
```

How can we see the year range in the column `year`?

```{r}
tidykids %>% count(year)
table(tidykids$year)
```

What are the variables listed in variable?

```{r}
count(tidykids, variable)
table(tidykids$variable)
```

See the `tidykids` codebook to understand what these variables represent:
https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html


The columns `raw`, `inf_adj`, and `inf_adj_per_child` are not named very clear. How can we rename them? Note that:

- raw refers to the raw amount spent
- inf_adj refers to the amount transformed to be in 2016 dollars for each year spent
- inf_adj_perchild refers to the amount transformed to be in 2016 dollars for each year per child in $1000s spent

```{r}
tidykids_clean <- tidykids %>%
  rename("amount_spent" = raw,
         "adjusted_amount_spent" = inf_adj,
         "adjusted_amount_per_child" = inf_adj_perchild)
```


Let's return the average number of K-12 students and amount spent per child in each state for the the year 2000 and later.

```{r}
tidykids_summarized <- tidykids_clean %>%
  filter(year >= 2000,
         variable == "PK12ed") %>%
  mutate(population = adjusted_amount_spent/adjusted_amount_per_child) %>%
  group_by(state) %>%
  summarize(avg_population = mean(population, na.rm=TRUE),
            avg_per_child = mean(adjusted_amount_per_child, na.rm=TRUE))
  
```


How can we visualize this as a bar chart?

<!-- Colors from https://bookdown.org/hneth/ds4psy/D-3-apx-colors-basics.html -->

```{r}
tidykids_summarized %>%
  arrange(-avg_per_child) %>%
  slice(1:10) %>%
  ggplot(aes(y=reorder(state, avg_per_child), 
             x=avg_per_child,
             #fill=state,
             fill=avg_per_child,
             label=scales::dollar(avg_per_child*1000)))+
  geom_col()+
  theme_minimal()+
  scale_fill_gradient(low="grey90", high="deeppink4")
```

