---
title: 'Assignment 2: College Majors'
author: "Wonderful Student"
date: '2022-12-16'
output: html_document
---
When complete, please submit this document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load your libraries here
```


```{r}
# Access the data here:
recent_grads <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")

```

## Exploration

Use the functions and techniques we have learned to become familiar with the data set.
Note, for a data dictionary, visit https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-10-16

```{r}

```

## Summarize the Data

Use the `tidyverse` to answer the following questions.
Save each answer as a data object to be used in your visualizations later.

1. Which major category has the largest total number of women?

```{r}
women <- recent_grads %>%
  group_by(Major_category) %>%
  summarize(sum = sum(Women))
```

2. Compare the average number of men and women across different major categories. What proportion of each major do mean and women comprise?

```{r}
# This data is not in the right shape, since summarize works across rows and men and women are instead in different columns. The code below will start you off. It will make the data set long, rather than wide. Use recent_grads_long to answer the question

recent_grads_long <- recent_grads %>%
  select(Major, Men, Women, Major_category) %>%
  pivot_longer(Men:Women, names_to = "sex", values_to="graduates")

majors_by_sex <- recent_grads_long %>%
  group_by(Major_category, sex) %>%
  summarize(mean = mean(graduates, na.rm=TRUE)) %>%
  group_by(Major_category) %>%
  mutate(pct = prop.table(mean))
```

3. Develop your own analysis that uses summarize

```{r}

```

## Visualize the Data

1. Using your first analysis, develop a **bar chart** that shows which major category has the largest total number of women


```{r}

```

2. Using your second analysis, develop a **stacked bar chart** that shows the proportion of mean and women by major.

```{r}

```


3. Using your own analysis from above, develop one additional bar chart of your choice. Try to go from "tired" to "wired" by using code from the examples provided!

```{r}

```


---

## Grading Rubric

| Criteria                                | Yes/No |
|:----------------------------------------|:--------|
| The file knits without errors           |   &check;    |
| Question 1 is answered correctly        |   []   |
| Question 2 is answered correctly        |   []   |
| There is a simple bar chart for Q1      |   []   |
| There is a stacked bar chart for Q2     |   []   |
| There is a third bar chart              |   []   |
