---
title: "Homework 4: Tidykids Intro"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

This assignment will be a little more open-ended than past assignments, given the growth in your confidence using R for _data wrangling_, and your initial efforts with visualizing your data.

## 1. Get set up

First, change the name in the YAML header. Load tidyverse. Create a code cell below to do this.

Then read the tidykids data into R, and assign a name/object to the data. Create a code cell below to do this.

## 2. Explore the data

Use one or more techniques (up to you) to explore the data, such as `glimpse()`, simply printing the name of the data, the `describe()` function from the {psych} package, etc. Do so below, adding one or more lines of interpretation of what you see (e.g., the data's dimensions, any issues with variable names, etc.).

```{r}

```

**INTERPRETATION:** [Please write response here.]

## 3. Graph 1: A Scatterplot

Create a scatterplot. For this plot, keep things simple. Use only (i.e., filter for):

- a single state,
- one expenditure of your choice (see the codebook for this - use only ONE type of expenditure)
- Put either `raw`, `inf_adj`, or `inf_adj_perchild` on the y-axis
- Put year on the x axis

In the next step, you'll extend this graph a bit. Note that the codebook is [here](https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html). As a tool, Healy Ch. 3 reading gives scatterplot code (borrow it, if you want)!

Let the open-endedness be fun, not a burden here. In your work, I am looking for effort, not perfect code or output.

```{r}

```

## 4. Graph 1: Modifications

Next, copy the code (and code chunk) from above to give you a starting point for several modifications. Specifically:

- Change the x- and y-axis labels (use the `labs()` function to add a layer to your ggplot2 code)
- Change the [theme](https://ggplot2.tidyverse.org/reference/ggtheme.html) (just pick one and add it to your code at the bottom)
- Filter the data to only include certain years (which years are entirely up to you - this is just practice with combining data wrangling and visualizing)
- Optionally, you can make any other changes you wish, but these are not necessary for now
- Add one or two sentences beneath the code chunk you have added interpreting what you found and what you might want to investigate next

```{r}

```

**INTERPRETATION:** [Please write response here.]

## 5. Graph 1: Add a Line

Copy your code above and paste it in the cell below. Then, add a line to the plot. To do this, use either `geom_line()` or `geom_smooth()`.

```{r}

```

## 6. Graph 2: Histogram

This may be more of a challenge. Consulting the {ggplot2} cheat sheet (see Canvas) as a support, create a histogram for a single expenditure (again, filter `expenditure` for a single type of expenditure). Change one of the axis labels and add a title and/or subtitle, again using the `labs()` function. You will have to choose one of `raw`, `inf_adj`, or `inf_adj_perchild` to consider. Some sample histogram code is provided in the Canvas module.

```{r}

```

## 7. Reach: Create _any graph of your choosing_ 

The requirements are:

- Use an expenditure (i.e., filter `expenditure` for a different expenditure type) that is different from any you used above.
- Include a different state than the one(s) you used above, or use multiple states or regions.
- Share _what_ you planned to show and _how_ you showed it (after your code chunk and output)
- Have fun with this! Any other changes (or absence of changes) are up to you!

```{r}

```

**WHAT I PLANNED TO SHOW:** [Please write response here.]

**HOW I PLANNED TO SHOW IT:** [Please write response here.]

## 8. Reflection
How did this go? What were the pain points? What did you enjoy? What would you like to learn more about? 
**REFLECTION:** [Please write response here.]


When complete, please knit the result to an HTML (be sure to add your name at the top!) and submit that for Assignment 4 in Canvas. 

Please note, you are only submitting the HTML output for this assignment.  

## 9. Bonus

Each variable in the `expenditure` column of the `tidykids` data set represents a different type of spending. Which type of adjusted spending per child, on average in $1,000s, is highest for Tennessee? 

**Make a simple bar chart showing this. Color the barchart by the average.**

Note that sample bar chart code is provided in the "A Practical Approach" portion of the lecture.

```{r}

```

**Rubric**

Name is added: 2 points
File knits to an HTML: 8 points
Code chunks have appropriate output: 15 points
Interpretations and reflection are added: 5 points
Bonus: 5 points
Total: 30 points
