---
title: "Example 2: Your Turn! (Two Continuous Variables)"
subtitle: "Planning a {ggplot}"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

We haven't learned `ggplot()` syntax yet -- that's next week! This is a **planning exercise**, following the same four steps we walked through in "Example 1" during lecture, so that when we do learn `ggplot2`, you have one model to help you think through what you're trying to build.

The difference from Example 1: that example compared a **discrete** variable (region) to a **continuous** one (spending), using `geom_col()`. This time, you'll plan a graph comparing **two continuous variables** -- which calls for a different `geom`.

## The Research Question

:::{style="background-color: #e0e0e0; padding: 10px; border-radius: 5px;"}
What is the relationship between year and per-child spending on K-12 education, for a state of your choice?
:::

## Step 1: Relevant Variables & Calculations

Just like in Example 1, break the RQ down into its parts.

1. What are the variables involved in this RQ? (Hint: look at the `expenditure` column in the [tidykids codebook](https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html) to see which numeric column represents "spending.")
2. For each variable, is it **discrete** or **continuous**?
3. Is there a calculation involved (e.g., a mean, like in Example 1), or are we just plotting the values as they are?

**YOUR ANSWER:**

- Variable 1 (discrete / continuous): [ANSWER HERE]
- Variable 2 (discrete / continuous): [ANSWER HERE]
- Calculation needed (if any, or if none): [ANSWER HERE]

## Step 2: Identify `geom`s with the Cheatsheet

Open the {ggplot2} cheatsheet (on Canvas). Find the section for **"Two Variables: Both Continuous."**

1. List 1-2 `geom`s from that section that could show the relationship between two continuous variables.
2. Which one do you think best answers *this* RQ, and why? (Hint: Multiple answers could work here. Also, since one variable is year, you might consider whether a second `geom` layered on top -- to help show a trend -- would be useful in addition to your first choice.) If you aren't sure, just make a guess. This isn't being graded for "correctness".

**YOUR ANSWER:**

- `geom`s available: [ANSWER HERE]
- Best choice for this RQ: [ANSWER HERE]
- Why: [ANSWER HERE]

## Step 3: Sketch

Just like the sketches in Example 1, draw a quick, rough sketch of what you expect this graph to look like *before* you build it. This can be on paper (take a photo) or in any drawing tool (e.g, https://excalidraw.com/) -- it doesn't need to be pretty.

Include:

- Which variable is on the x-axis, which is on the y-axis. Include labels!
- What each point/mark on the graph represents (hint: what is the unit of observation here?)
- Roughly what pattern you'd *expect* to see (increasing? decreasing? flat? something else?) -- this is a prediction, not a right/wrong answer

**[Upload your sketched image to Canvas as a second file with your rendered .html.]**

## Step 4: Plan the Data Wrangling

This is the part you already know how to do! Using {dplyr} functions we've learned, plan out -- in words first, then in code -- how you'd get the data into the shape needed for the graph you sketched above.

Think about:

- What (likely two things) do you need to `filter()` for?
- Which of the three numeric spending columns (`raw`, `inf_adj`, or `inf_adj_perchild`) makes the most sense to use for this RQ, and why?

Write your plan in words first:

**PLAN:** [Please write response here.]

Then write the code to actually produce that wrangled dataset (do **not** write any `ggplot()` code yet -- just get the data ready):

Load tidyverse in this cell.
```{r load_packages}
library(tidyverse)
```

Read in the data in this cell.
```{r load_data}

```

Execute your wrangling plan in this cell. Keep only the columns you want to inform your plot (i.e., you'll drop some variables here).
```{r wrangle}

```


Print the first several rows (that is, type the name of the object, use `print()`), so the .html shows a bit of the data when rendered) of your wrangled dataset below to confirm it looks the way you expect (one row per year, for your chosen state and expenditure type):

```{r print_data}

```

## Challenge (Optional)

If you want, take your wrangled data and create your plot. If you aren't sure how to make a ggplot yet, that's fine. You will soon in the next couple of weeks. This is completely optional.

```{r challenge}

```

## Reflection

1. Looking at your wrangled data (not necessarily a graph yet, unless you did the challenge), what early hints do you see about the relationship between year and spending?
2. How did this go? Remember, this is just one way to plan out your plot. Some people reorder these steps, and others have a completely different approach that works for them, and that's great!

**REFLECTION:** [Please write response here.]


