---
title: "Untitled"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
    out-width: "100%"
---

<!--Load in your packages. -->
```{r packages}

```

### 1. Reading in Data
- You may use your own data, tidykids data, starwars data, or palmerpenguins data.
```{r read_in_data}

```

### 2. Wrangling Data
```{r wrangle_data}

```

### 3. Creating a Table with {gt}
Requirements for table:

- A title
- A stub
- A source note
- Either Markdown `md()` or HTML `html()` styling
- At least one `tab_style()` argument
```{r create_table}

```

### 4. Adding in Bonus Features
+ 5 pts. for using idea from Tutorial #3
+ 5 pts. for using idea from Tutorial #4
```{r table_with_bonus_features}

```

***REQUIRED DOCUMENTATION FOR BONUS!***
Which feature did you implement...

- **From Tutorial #3:** [ANSWER HERE]
- **From Tutorial #4:** [ANSWER HERE]

### 5. Reflection
How did this assignment go? What did you learn? What would you do differently next time? 

**Reflection:** [Please write your reflection here.]
