---
title: 'Assignment 1: tidykids'
author: "Your Name Here"
date: "Date"
output: html_document
---

## Instructions

Each variable in the `variable` column of the `tidykids` data set represents a different type of spending. Which type of adjusted spending per child, on average in $1,000s, is highest for Tennessee? 

**Make a simple bar chart showing this. Color the barchart by the average.**


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load packages here
library(tidyverse)
library(tidykids)

```




```{r}
# simple example
tn_data <- tidykids %>%
  filter(state == "Tennessee") %>%
  group_by(variable) %>%
  summarize(mean = mean(inf_adj_perchild*1000, na.rm=TRUE))

tn_data %>%
  ggplot(aes(y=reorder(variable, mean), 
             x=mean,
             fill=mean))+
  geom_col()
```


---

## Grading Rubric

| Criteria                                | Yes/no |
|:----------------------------------------|:--------|
| The code answers the question           |   &check;    |
| There is a bar chart                    |   x   |
| The chart is colored by a numeric value |      |
| The code runs when file is knit         |      |
