---
title: "Week 3 - Walkthrough"
author: "Your name"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1: Core R functions

*1.1: Load the tidyverse*

```{r}
library()
```

*1.2: Read a CSV file with the data you are analyzing into your R session*

```{r}
read_csv("")
```

*1.3: Assign a name to the data you read into your R session using the assignment operator*

```{r}
<- read_csv("")
```

*1.4: glimpse() the data you assigned a name to*

```{r}
glimpse()
```

*1.5: Replace d with the name of the data you loaded to glimpse the data in an alternate way*

```{r}
d %>% 
  glimpse()
```

## 2: Working with variables (columns)

*2.1: rename() one variable in your data, with the aim of making the variable easier to type or understand*

```{r}
d %>% 
  rename("" = )
```

*2.2: Using the code above, assign a name to the data with the renamed variable; glimpse the newly named data to check that it worked*

```{r}

```

*2.3: select() three variables in your data and assign a name to the resulting data set that is returned*

```{r}
d %>% 
  select()
```

*2.4: Using the new data frame you named in step 2.3, arrange() the rows of your data based on the values of a variable of your choosing*

```{r}
d %>% 
  arrange()
```

*2.5: Again using the data you named in step 2.3, create a new variable, replacing new_var with a name you provide, that sums together two columns*

```{r}
 %>% 
  mutate(new_var = )
```

## 3: Working with rows (observations) and using logical operators

*3.1: filter() the data you read based on the values of a variable of your choosing so that only rows less than or equal to a specified value are returned, replacing d here and throughout with the name of the data you loaded*

```{r}
d %>% 
  filter()
```

*3.2: filter() the data you read so that only a value equivalent to either one of two character strings is returned, replacing d here and throughout with the name of the data you loaded*

```{r}
d %>% 
  filter()
```

*3.3: count() the number of times values for a variable of your choosing occur in your data*

```{r}
d %>% 
  count()
```

*3.4: Group the rows in your data by replacing my_group with the name of a variable of your choosing and find the mean() of the values for each group*

```{r}
d %>% 
  group_by(my_group) %>% 
  summarize(mean_value = mean())
```

*3.5: Group the rows in your data by replacing my_group with the name of a variable of your choosing and find the sum() of the values for each group, then arranging the resulting values by a variable you specify*

```{r}
d %>% 
  group_by(my_group) %>% 
  summarize(mean_value = ) %>% 
  arrange()

## 4: Knit and share your report

When complete, please knit the result to an HTML and submit that for the Week 3 Walkthrough in Canvas. 

Nice job!
