---
title: "Exploring gapminder with dplyr: Assignment 3"
author: "your name"
date: '2024-09-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1: Core R functions

*First, load the tidyverse in the code chunk below*

```{r}

```

*Next, read in the gapminder CSV data and assign it a name*

```{r}

```

*Last, glimpse the data you read in and named*

```{r}

```

## 2: Working with variables (columns)

*Use select to choose three variables of your choosing*

```{r}

```

*Using the original data (not the one with three variables of your choosing), rename the pop variable to be a bit easier to understand (what the variable represents), assigning a name to the data that results*

```{r}

```

## 3: Working with rows (observations) and using logical operators

*Filter the data to only include three countries of your choosing, assigning a name to the data that results*

```{r}

```

*Filter the data to only values above or below a year of your choosing, assigning a name to the data that results. Add a sentence interpreting what you found.*

```{r}

```

## 4: Scavenger hunt

*Using the full dataset of observations, which country-year combination has the highest life-expectancy? Arrange the appropriate variable in descending order to see for which country and year its value is greatest. Add a sentence interpreting what you are noticing from your output below the code chunk*.

```{r}

```

*For a year of your choosing, which continent has the most countries?* 

```{r}

```

*What was the GDP per capita of the U.S. in 1982 and 1992?*

```{r}

```

## 5: *fin*

*Freestyle: Use any of the functions you have used to investigate the data. Add a few sentences on what you did and what you found. You can think bigger picture here about the data and what you can (or cannot!) learn from it*

```{r}

```

*Optionally, create a ggplot2 plot with the data.*

```{r}

```

## 6: Reflect, knit, and share your report

How did this assignment go? What went well --- or what was tricky? Briefly (a sentence or two is fine!) reflect below.

**Reflections:**

When complete, please knit the result to an HTML (be sure to add your name at the top!) and submit that for Assignment 3 in Canvas. Please note, you are only submitting the HTML output for this assignment.  

Nice job!

**Rubric**

Name is added: 2 points
File knits to an HTML: 8 points
Code chunks have appropriate output: 15 points
Interpretations and reflection are added: 5 points
Total: 30 points
