---
title: "Week 3 - Walkthrough"
author: "Josh"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

## 1: Core R functions

*1.1: Load the tidyverse*

```{r}
# install.packages("tidyverse) - make sure to comment out install.packages
library(tidyverse)
```

*1.2: Read a CSV file with the data you are analyzing into your R session*

```{r}
read_csv("gapminder.csv")
```

*1.3: Assign a name to the data you read into your R session using the assignment operator*

```{r}
gap <- read_csv("gapminder.csv")

gap <- gap %>% 
  select(-...1)
```

*1.4: glimpse() the data you assigned a name to*

```{r}
glimpse(gap)
```

*1.5: Replace d with the name of the data you loaded to glimpse the data in an alternate way*

```{r}
gap %>% 
  glimpse()

```

## 2: Working with variables (columns)

*2.1: rename() one variable in your data, with the aim of making the variable easier to type or understand*

```{r}
# specify what we rename the variable to within ""

gap %>% 
  rename("gdp" = gdpPercap,
         "life_exp" = lifeExp)
```

*2.2: Using the code above, assign a name to the data with the renamed variable; glimpse the newly named data to check that it worked*

```{r}
gap <- gap %>% 
  rename("gdp" = gdpPercap,
         "life_exp" = lifeExp)
```

*2.3: select() three variables in your data and assign a name to the resulting data set that is returned*

```{r}
gap_subset <- gap %>% 
  select(country, year, life_exp)
```

*2.4: Using the new data frame you named in step 2.3, arrange() the rows of your data based on the values of a variable of your choosing*

```{r}
gap %>% 
  arrange(desc(life_exp))
```

*2.5: Again using the data you named in step 2.3, create a new variable, replacing new_var with a name you provide, that sums together two columns*

```{r}
gap %>% 
  mutate(life_exp_plus_gdp = life_exp + gdp)
```

## 3: Working with rows (observations) and using logical operators

*3.1: filter() the data you read based on the values of a variable of your choosing so that only rows less than or equal to a specified value are returned, replacing d here and throughout with the name of the data you loaded*

```{r}
gap_filtered <- gap %>% 
  filter(year == 2007)
```

*3.2: filter() the data you read so that only a value equivalent to either one of two character strings is returned, replacing d here and throughout with the name of the data you loaded*

```{r}
gap %>% 
  filter(continent == "Asia" | continent == "Europe")
```

*3.3: count() the number of times values for a variable of your choosing occur in your data*

```{r}
gap %>% 
  count(year)

gap <- gap %>% 
  mutate(year = as.integer(year))
```

## 4: Knit and share your report

When complete, please knit the result to an HTML and submit that for the Week 3 Walkthrough in Canvas. 

Nice job!
