---
title: "Exploring Gapminder Data with {dplyr}"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---

## Part A: Core R Functions

#### Load Packages
1. Load {tidyverse} in the code chunk below. No need to install it again, though. You already did this in a previous assignment.

```{r}

```


#### Read in Data
2. Read in the gapminder CSV data and assign it a name. Use the `read_csv()` function to do this.

```{r}

```

#### Review the Data
3. `glimpse()` the data you read in and named.

```{r}

```


## Part B: Working with Variables (Columns)

#### Selecting Variables
4. Use `select()` to choose three variables of your choosing. Look briefly at the next question. Should you store the new dataset with three selected variables to the original object?

```{r}

```

#### Renaming Variables
5. Using the original data (not the one with three variables of your choosing), rename the pop variable to be a bit easier to understand (what the variable represents), assigning a new object/name to the data that results.

```{r}

```

## Part C: Working with Rows (Observations) and Using Logical Operators

#### Filtering Rows With Strings
6. Filter the data to only include three countries of your choosing, assigning a new object name to the data that results.

```{r}

```

#### Filtering Rows with Numeric/Integer Values
7. Filter the data to only values above or below a year of your choosing, assigning a name to the data that results. Add a sentence interpreting what you found.

```{r}

```

8. **FREE RESPONSE:** [Please write your sentence interpretation here.]

## D: Scavenger Hunt

9. Using the full dataset of observations, which country-year combination has the highest life-expectancy? Arrange the appropriate variable in descending order to see for which country and year its value is greatest. Add a sentence interpreting what you are noticing from your output below the code chunk.

```{r}

```

10. **FREE RESPONSE:** [Please write your sentence free response concerning your noticings here.]

11. For a year of your choosing, which continent has the most countries? 

```{r}

```

12. What was the GDP per capita of the U.S. in 1982 and 1992?

```{r}

```

## E: Freestyle

13. *Freestyle:* Use any of the functions you have used to investigate the data. Add a few sentences on what you did and what you found. You can think bigger picture here about the data and what you can (or cannot!) learn from it.

```{r}

```

## F: Optional Section

14. *Optional:* Create a {ggplot2} plot with the data.

```{r}

```

## G: Reflect, knit, and share your report (Required)

How did this assignment go? What went well --- or what was tricky? Briefly (a sentence or two is fine!) reflect below.

**REFLECTION:** [Please write your reflection here.]

When complete, please render the file as .html (be sure to add your name at the top!) and submit it for Assignment 3 in Canvas. Please note, you are only submitting the HTML output for this assignment.  

**Nice job!**

## Rubric (30 pts.)

- Name is added: 2 points
- File knits to an HTML: 8 points
- Code chunks have appropriate output: 15 points
- Interpretations and reflection are added: 5 points
