---
title: "dplyr Titanic practice"
author: "Kelly Boles"
date: "2024-09-01"
output: html_document
---

# Instructions
1. Adjust the setup chunk to include `warning=FALSE` and `message=FALSE` to suppress warnings and messages 
2. Put all team member names in the author YAML field above
3. Answer the following questions using the `Titanic-Dataset.csv` dataset
4. Run each code chunk and make sure the code block runs without errors as you go
5. Think carefully about which chunks to assign, either to an existing object or
a new one

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The `tidyverse` package should already be installed on your machine. Now, load `tidyverse` in the code chunk below.
```{r load_tidyverse}

```

Read in the Titanic data from the `Titanic-Dataset.csv` file. It is in the zip file you downloaded.

```{r load_data}

```

In the Estrellado reading from Week 2, the authors introduced the `clean_names()` function from the `janitor` package (https://datascienceineducation.com/c06). Use this function to clean the variable names in the dataset. Hint: It's good practice to load all packages at the beginning of your script (i.e. go back and load it with tidyverse). In the code chunk below, use the `clean_names()` function to clean the variable names.

```{r clean_names}

```


<!-- Data Dictionary / Codebook for the Titanic Data is here: https://www.kaggle.com/c/titanic/data -->

Pull up the codebook for the `titanic` dataset using the url above (copy/paste it into your browser). Then, in the
code block below, use `glimpse()` to preview the dataset. You may also want to use View() to see the dataset in a
spreadsheet format or use str() to see more about its structure. (Note: Please use `View` in the Console only - it causes knitting errors) After reviewing the dataset, answer the following question.

QUESTION: How many columns/variables are in the dataset?

ANSWER: 12

```{r glimpse}

```

Next, let's drop the variables that are not of use to us in this analysis. Drop the `PassengerId`, as it's a duplicate of the row number, anyway. After dropping the variable, use `glimpse()` to confirm that the variable was dropped. How many columns/variables are in the dataset now?

ANSWER:

```{r drop_passengerid}

```

Now, let's rename a variable name to make it more clear. Rename the `Pclass` variable to `Class`.

```{r rename_pclass}

```

For many of the passengers, we have their age. How many passengers DO NOT have a known age? After running the needed code, please write your answer here.

ANSWER: 177

```{r count_na_age}

```

Let's create a new variable called `age_group` that has a value of "child" if the passenger is under 13 years old, "teen" if the passenger is 13-18 (not including 18), and "adult" if 18 or over. Note: You are creating a new variable based on an existing variable.

```{r create_age_group}

```

Let's create a new variable called `family_size` that is the sum of the `sib_sp` and `parch` variables. This will give us the total number of family members on board for each passenger.

```{r create_family_size}

```

Let us create a third and final variable called `famsize_group` that categorizes the `family_size` variable into three groups: "single" if the passenger has no family members on board, "small" if the passenger has 1-3 family members on board, and "large" if the passenger has 4 or more family members on board.

```{r create_famsize_group}

```

Group and summarize the data to find the average survival rate by `class` and `age_group`. Also, count the number of people in each group. What is the survival rate for children in first class? How does it compare to other groups? NOTE: You may wish to save this output to a new object to reference later - maybe something like `surv_rates_age_class`.

ANSWER:

```{r surv_rates_age_class}

```

Let's drop the `NA` rows for `age_group` from the last output.

```{r drop_na_age_group}

```

Finally, let's arrange the data by survival rate in descending order. This will allow us to see which groups had the highest survival rates.

```{r arrange_survival_rate}

```

Each person should knit this file to HTML and upload it to Canvas.