---
title: "Week 13 Distributions Activity"
author: "Awesome Student"
date: '2023-04-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

For this assignment, we are going to look at tuition and fees by college/university for 2018-2019, along with school type, degree length, state, in-state vs out-of-state from the [Chronicle of Higher Education](https://www.chronicle.com/interactives/tuition-and-fees.

```{r}

tuition_cost <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-10/tuition_cost.csv')
```

## Become Familiar with the Data

As with any data set, your first step is to become familiar with the variables, values, and structure of the data:

```{r}

```


## Building Distributions

### What does the distribution of in-state tuition look like across all states and college/university types? Make a simple histogram and a simple boxplot.

```{r}
hist(tuition_cost$in_state_tuition)
```


```{r}
boxplot(tuition_cost$in_state_tuition)
```

Write a sentence or two to describe your findings:


### How does the distribution of in-state tuition vary by college/university types? Use `ggplot` to make a histogram. Use `fill` and a facet.

```{r}
ggplot(tuition_cost, aes(x=in_state_tuition, fill=type))+
  geom_histogram(position = "identity")+
  facet_wrap(~type)
```

Write a sentence or two to describe your findings:


### Let's look at the distribution of *out-of-state* tuition across 10 states. Decide on a method to select 10 states (top 10 highest average tuitions, 10 states in the southeast, etc.). Then use the `ggridges` package to show the distribution of tutition for each state. 

Use the [`ggridges` documentation](https://cran.r-project.org/web/packages/ggridges/vignettes/introduction.html) to do the following:

- Make the density ridges overlap slightly with the ones above/below
- Fill the density curve with a gradient and set the color of the gradient
- Add a median line to each state's density curve
- **Bonus**: Don't let the ridges touch AND add a raincloud plot below each ridge

All of these can be done by simply following and copying code from the `ggridges` documentation

```{r}
tuition_cost %>%
  inner_join(
    tuition_cost %>%
    drop_na(state) %>%
    group_by(state) %>%
    summarize(mean = mean(out_of_state_tuition)) %>%
    slice_max(order_by = mean, n=10)) %>%
  ggplot(aes(x=out_of_state_tuition, y=state, fill=stat(x)))+
  geom_density_ridges_gradient(scale=.5,
                               quantile_lines = TRUE, quantiles = 2,
                               jittered_points = TRUE, position = "raincloud")+
  scale_fill_viridis_c(name = "Temp. [F]", option = "C")
```


