---
title: "Week 10 Assignment"
author: ""
date: ''
output: html_document
---
<!-- Add options to YAML header and setup chunk. -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r package-install}
library(tidyverse)
library(patchwork)
```

This week's assignment is quite simple. You are going to re-use some of your old graphs in order to practice making compound graphics and small multiples and using annotations. Throughout, you are not expected to pay attention to all of the aesthetic elements of the plot, but please ensure that the plots are interpretable and accessible through your use of themes, color, labels, text and fonts, etc.

## Compound Plots with patchwork

Using a previous data set and related analyses and/or visualizations, combine separate plots using `patchwork`. For some additional functionality (or examples), check out its documentation: https://patchwork.data-imaginist.com/index.html



## Small Multiples with facet_wrap()

Using a previous data set (and analysis), develop a data visualization that uses small multiples. To add a little pizazz and style your facets, consider consulting these resources:

- http://www.cookbook-r.com/Graphs/Facets_(ggplot2)/
- https://www.datanovia.com/en/blog/how-to-change-ggplot-facet-labels/


## Annotations

Again using a previous data set and related analyses and/or visualizations, add two or more annotation layers to a plot OR use gghighlight.


```{r}

```

## Reflection

Important note: After you knit, check the HTML file. 

- Does it appear as you intended? ANSWER HERE
- Does any output print that is too long? ANSWER HERE
- Do your name and date appear? ANSWER HERE

Share any questions you have in Canvas about fine-tuning your .Rmd output.

And, please answer this question: How did this assignment go? What went well and what was a challenge? Please add 1-2 sentences.

REFLECTION GOES HERE:

## 4. Submit

Please be sure to add your name and the date. Knit and submit!

**Rubric**

Name is added: 2 points
File knits to an HTML: 4 points
patchwork plot: 6 points
faceted plot: 6 points
Annotated plot: 6 points
Attention to the aesthetics are considered: 6 points

Total: 30 points
