---
title: "Week 3 Slides"
subtitle: "How do I wrangle data?"
author: "**Joshua Rosenberg and Isabella Velásquez**"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_duo_accent(
  primary_color = "#FF8200",
  secondary_color = "#58595B",
  link_color = "blue",
  title_slide_text_color = "#222943",
  title_slide_background_color = "#ededed",
  title_slide_background_image = "https://brand.utk.edu/wp-content/uploads/2019/02/University-HorizRightLogo-RGB.png",
  title_slide_background_position = "bottom",
  title_slide_background_size = "30%"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, echo=FALSE}
# then load all the relevant packages
pacman::p_load(pacman, knitr, tidyverse, readxl)
```

```{r xaringanExtra-clipboard, echo=FALSE}
# these allow any code snippets to be copied to the clipboard so they 
# can be pasted easily
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
  ),
  rmarkdown::html_dependency_font_awesome()
)
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

# Purpose and Agenda

This week, we answer the following question: What's this class all about?

## What we'll do in this presentation

- Recap
- A bit more introductions
- Reading discussion in whole group chat
- Key concept #1 - dplyr verbs
- Key concept #2 - stringr and forcats
- Code-along
- What’s next

---

# Recap

Last week, we:

  - Reviewed the [syllabus](https://docs.google.com/document/d/1FItWUb46iL5cxvFW6TIf02BDtt7Q0I_OE-aS_HhOSIw/edit)
  - Discussed two key concepts: #1) the repetitive structure of the coruse and 2) how the theoretically-focused aspect of this course will build on your intuitions
  - Did a code-along that led into the assignment
  - Read a chapter by Healy

---

# A bit more introductions

## Josh

A few projects...

- CREDIBLE
- konfound
- T(CA)^2
- Social media and students' right to privacy
- ESM

## Isabella

Introduction! And office hours next week (and four classes)

https://utk.instructure.com/courses/196893/external_tools/1509

---

# Reading discussion

Link to [reading](https://socviz.co/gettingstarted.html#gettingstarted)

- What is one thing you took away from this reading about how and why R Markdown and R work the way they do?
- What was confusing about the reading?

https://jamboard.google.com/d/169YPYiQ7z39Pm1XFxxaEvu-cBJs5FkXjNTbjjyKHgec/edit?usp=sharing


---

# Key concept #1: Core dplyr "verbs"

- `rename()`
- `select()`
- `filter()`
- `count()`
- `glimpse()`

**We'll explore these in much more detail in the code-along**

---

# Key Concept #2: stringr and forcats

These are super handy:

**stringr**: an R package for working with character strings, e.g. `str_detect()`
**forcats**: an R package for working with factors, e.g. `fct_relevel()`

---

# stringr with dplyr

```{r, echo = TRUE, eval = FALSE}
library(tidyverse)

# Sample data
people <- tibble(
  name = c("John Doe", "Jane Doe", "Alice Johnson", "Bob Smith"),
  email = c("john.doe@example.com", "jane.doe@example.net", "alice.j@example.org", "bob.smith@example.com")
)

people %>%
  mutate(
    is_alice = str_detect(name, "Alice"), # detecting a particular string
    domain = str_extract(email, "@.*$"), # Extracting email domains
  )

```

---

# forcats

```{r, echo = TRUE, eval = FALSE}
# Sample data
survey <- tibble(
  respondent = c(1, 2, 3, 4, 5),
  satisfaction = c("Satisfied", "Neutral", "Dissatisfied", "Very Satisfied", "Neutral"),
                        levels = c("Very Dissatisfied", "Dissatisfied", "Neutral", "Satisfied", "Very Satisfied")
)

# Using forcats functions within dplyr to manipulate factors
survey %>%
  mutate(
    satisfactor = as.factor(satisfaction),
    satisfaction_reordered = fct_relevel(satisfaction, "Very Satisfied", "Satisfied"), # Reordering factor levels
    satisfaction_collapsed = fct_collapse(satisfaction, Other = c("Neutral", "Dissatisfied", "Very Dissatisfied")) # Collapsing certain levels into 'Other'
  ) %>%
  count(satisfaction_collapsed) # Counting the occurrence of each level

```

---

# R Data Wrangling Code-along

- Download the `Week 3 Code-along.Rmd` file
- Save this to a `week-3` folder in your RStudio project
- Copy over the **gapfinder.csv** data into the `week-3` folder (*n.b.*, you can have a single copy of your data for your entire project; this is just to keep things easy for now)
- Open the `Week 3 Code-along.Rmd` file and ... code-along!

---

# What's next?

.panelset[


.panel[.panel-name[Weekly Assignment]

- This week, we'll build on what we've done in the code-along
]

.panel[.panel-name[Data]

- We'll again be using [gapminder](https://www.gapminder.org/) data

]

.panel[.panel-name[Reading(s)]

> Knaflic (2015), introduction and c1


]

.panel[.panel-name[Office hours]

- Friday at 1:00 pm with Josh, via the class Zoom 
- Also via calendly from Josh: https://calendly.com/joshuamrosenberg/15-minute-meeting

]

]

---

# Check out

- What's one thing you took away from today?
- What's one thing you want to learn more about?
