---
title: "Assignment 4"
name: "xx"
output: html_document
date: "xx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment will be a little more open-ended than past assignments, given the growth in your confidence using R for _data wrangling_, and your initial efforts with in visualizing your data.

## 1. Get set up

First, change the name and date in the front matter. Then, save this file into a folder with the tidykids data, which can be found on Canvas (or may already be downloaded). 

Then read the tidykids data into R, and assign a name to the data. 

## 2. Explore the data

Use one or more techniques (up to you) to explore the data, such as `glimpse()`, simply printing the name of the data, the `describe()` function from the psych package, etc. Do so below, adding one or more lines of interpretation of what you see (e.g., the data's dimensions, any issues with variable names, etc.).

```{r}

```

## 3. Graph 1: A scatterplot

Similar to what we created in the walkthrough, create a scatterplot. For this scatter plot, keep things simple, doing so for a single state and a single variable. Note that in the next step, you'll extend this graph a bit. Note that the codebook is here: https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html

Let the open-endedness be fun, not a burden here - in your work, I am looking for effort, not perfect code or output.

```{r}

```

## 4. Graph 2: Modifications

Next, copy the code (and code chunk) from above to give you a starting point for several modifications. Specifically:

- Change the x- and y-axis labels (use the `labs()` function to add a layer to your ggplot2 code)
- Change the theme
- Filter the data to only include certain years (with the specific years entirely up to you - this is just practice with combining data wrangling and visualizing)
- Optionally, you can make any other changes you wish, but these are not necessary for now
- Add one or two sentences beneath the code chunk you have added interpreting what you found and what you might want to investigate next

## 5. Add a line

Copy the code above, adding either a connecting line or an interpolated line to your points. 

## 6. Graph 4: Histogram

This may be more of a challenge. Consulting the ggplot2 cheat sheet (see the module in Canvas) as a support, create a histogram for a single variable. Change one of the axis labels and add a title and/or subtitle, again using the `labs()` function.

```{r}

```

## 7. Reach: Create _any graph of your choosing_ 

The requirements are:

- State _who_ your intended audience is (before any code in a code chunk)
- Use a variable that is different from any you used above
- Include a different state than the one(s) you used above, or use multiple states
- Share _what_ you planned to show and _how_ you showed it (after your code chunk and output)
- Have fun with this! Any other changes (or absence of changes) are up to you!

## 8. Reflection

When complete, please knit the result to an HTML (be sure to add your name at the top!) and submit that for Assignment 3 in Canvas. 

Please note, you are only submitting the HTML output for this assignment.  

If you see a warning at the top of your output related to your version of packages, it likely means you should update R. Please do this!

Nice job on this - this was close to an authentic analysis, and we're just getting started with ggplot2!

## 9. Bonus

Each variable in the `variable` column of the `tidykids` data set represents a different type of spending. Which type of adjusted spending per child, on average in $1,000s, is highest for Tennessee? 

**Make a simple bar chart showing this. Color the barchart by the average.**

```{r}

```

**Rubric**

Name is added: 2 points
File knits to an HTML: 8 points
Code chunks have appropriate output: 15 points
Interpretations and reflection are added: 5 points
Bonus: 5 points
Total: 30 points
