---
title: "Assignment 4"
author: "xx"
output: html_document
date: "xx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This assignment will be a little more open-ended than past assignments, given the growth in your confidence using R for _data wrangling_, and your initial efforts with visualizing your data.

## 1. Get set up

First, change the name and date in the YAML front matter. 

Then read the tidykids data into R, and assign a name to the data. 

## 2. Explore the data

Use one or more techniques (up to you) to explore the data, such as `glimpse()`, simply printing the name of the data, the `describe()` function from the psych package, etc. Do so below, adding one or more lines of interpretation of what you see (e.g., the data's dimensions, any issues with variable names, etc.).

```{r}

```

INTERPRETATION:

## 3. Graph 1: A scatterplot

Create a scatterplot. For this plot, keep things simple. Use only a single state, one variable of your choice (i.e., filter `variable` to focus only on ONE expenditure type) on the y-axis and year on the x. Note that in the next step, you'll extend this graph a bit. Note that the codebook is here: https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html

Let the open-endedness be fun, not a burden here - in your work, I am looking for effort, not perfect code or output.

```{r}

```

## 4. Graph 2: Modifications

Next, copy the code (and code chunk) from above to give you a starting point for several modifications. Specifically:

- Change the x- and y-axis labels (use the `labs()` function to add a layer to your ggplot2 code)
- Change the [theme](https://ggplot2.tidyverse.org/reference/ggtheme.html)
- Filter the data to only include certain years (with the specific years entirely up to you - this is just practice with combining data wrangling and visualizing)
- Optionally, you can make any other changes you wish, but these are not necessary for now
- Add one or two sentences beneath the code chunk you have added interpreting what you found and what you might want to investigate next

```{r}

```

INTERPRETATION:

## 5. Add a line

Copy the code above, adding either a connecting line(`geom_line`) or an interpolated line(`geom_smooth`) to your points. 

## 6. Graph 4: Histogram

This may be more of a challenge. Consulting the ggplot2 cheat sheet (see Canvas) as a support, create a histogram for a single variable (again, filter `variable` for a single type of expenditure). Change one of the axis labels and add a title and/or subtitle, again using the `labs()` function.

```{r}

```

## 7. Reach: Create _any graph of your choosing_ 

The requirements are:

- State the research question you are addressing with your plot
- Use a variable (i.e., filter `variable` for a different expenditure type) that is different from any you used above
- Include a different state than the one(s) you used above, or use multiple states
- Share _what_ you planned to show and _how_ you showed it (after your code chunk and output)
- Have fun with this! Any other changes (or absence of changes) are up to you!

```{r}

```

RESEARCH QUESTION:

WHAT I PLANNED TO SHOW:

HOW I SHOWED IT:

## 8. Reflection
How did this go? What were the pain points? What did you enjoy? What would you like to learn more about? 


When complete, please knit the result to an HTML (be sure to add your name at the top!) and submit that for Assignment 4 in Canvas. 

Please note, you are only submitting the HTML output for this assignment.  

## 9. Bonus

Each variable in the `variable` column of the `tidykids` data set represents a different type of spending. Which type of adjusted spending per child, on average in $1,000s, is highest for Tennessee? 

**Make a simple bar chart showing this. Color the barchart by the average.**

```{r}

```

**Rubric**

Name is added: 2 points
File knits to an HTML: 8 points
Code chunks have appropriate output: 15 points
Interpretations and reflection are added: 5 points
Bonus: 5 points
Total: 30 points
