---
title: "Week 2 `tidykids` Walk Through"
author: "Awesome Student"
date: '2022-12-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
remotes::install_github("jrosen48/tidykids")
```


How can we load the `tidykids` package?

```{r}

```



How can we view the data in R Studio as a spreadsheet?

```{r}

```


How can we view the first 10 rows of tidykids?

```{r}

```

How about the last 5 rows?

```{r}

```


How can we see the structure of the data?

```{r}

```

How can we list the column names?

```{r}

```

How can we see the year range in the column `year`?

```{r}

```

What are the variables listed in variable?

```{r}

```

See the `tidykids` codebook to understand what these variables represent:
https://jrosen48.github.io/tidykids/articles/tidykids-codebook.html

The columns `raw`, `inf_adj`, and `inf_adj_per_child` are not named very clear. How can we rename them? Note that:

- raw refers to the raw amount spent
- inf_adj refers to the amount transformed to be in 2016 dollars for each year spent
- inf_adj_perchild refers to the amount transformed to be in 2016 dollars for each year per child in $1000s spent

```{r}

```

**Reach --- this next part is quite a bit more challenging!**

Let's return the average number of K-12 students and amount spent per child in each state for the the year 2000 and later.

```{r}

  
```
