---
title: "Highlighter"
author: "Student"
date: '2023-02-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# The Data

```{r}
phd_field <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-02-19/phd_by_field.csv")
```

The data comes from the Survey of Earned Doctorates and is provided via [a #TidyTuesday repo](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-02-19).

### Explore the data set

```{r}

```


# Chart 1 - A single line

Make a *simple* line chart of total number of PhD graduates per year

```{r}
phd_field %>%
  group_by(year) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=year, y=n))+
  geom_line()
```


# Chart 2 - Area Under the Line

Change this line chart so that the line is slightly thicker and there is a "cyan4" shaded area under the line. Set the limits to 1000 under the min and over max of the data

```{r}
year_summary <- phd_field %>%
  group_by(year) %>%
  summarize(n = sum(n_phds, na.rm=TRUE))
  
year_summary %>%
  ggplot(aes(x=as.factor(year), y=n, group=1))+
  geom_line(size=1.2)+
  geom_area(fill="cyan4")+
  coord_cartesian(ylim = c(min(year_summary$n)-1000, max(year_summary$n)+1000))
```

# Chart 3 - One Line Per Group

Make a line chart like above, however, there should be one line per `broad_field`. Drop the "Other" category. There should be 6 categories total.

```{r}
phd_field %>%
  filter(broad_field != "Other") %>%
  group_by(year, broad_field) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=as.factor(year), y=n, color=broad_field,
             group=broad_field))+
  geom_line()
```

# Chart 4 - Labelled Lines

Let's use `gghighlight` to label each line. Simply add `gghighlight()` to the end of the code you wrote above. The default option is kind of ugly. You can alter the `label_params` following examples from [here](https://ggrepel.slowkow.com/articles/examples.html) OR you can try different label styles as listed under `line_label_type` [here ](https://yutannihilation.github.io/gghighlight/reference/gghighlight.html)

```{r}
library(gghighlight)

phd_field %>%
  filter(broad_field != "Other") %>%
  group_by(year, broad_field) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=as.factor(year), y=n, color=broad_field,
             group=broad_field))+
  geom_line()+
  gghighlight(line_label_type = "text_path")
```
# Chart 5 - Facet Per Broad Field

Using the code from Chart 3 above, facet the chart so there is one line per facet. There should be 2 rows. Remove the legend. Rotate the year text by 90.

```{r}
phd_field %>%
  filter(broad_field != "Other") %>%
  group_by(year, broad_field) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=as.factor(year), y=n, color=broad_field,
             group=broad_field))+
  geom_line()+
  facet_wrap(~broad_field, nrow=2)+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))
```

# Chart 6 - Facet and Highlight

Add `gghighlight` to the code from Chart 5 and remove the text labels.

```{r}
phd_field %>%
  filter(broad_field != "Other") %>%
  group_by(year, broad_field) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=as.factor(year), y=n, color=broad_field,
             group=broad_field))+
  geom_line()+
  gghighlight(use_direct_label=FALSE)+
  facet_wrap(~broad_field, nrow=2)+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))
```

# Final Plot

Awesome! You are now a **highlighter**.

Take the code from above and give it a makeover:
- Change the line colors
- Add a title and other labels
- Remove the strip background and make the panel titles bold
- Change the panel background to white.
- Try unrotating the years and see if you like `scale_x_discrete(guide = guide_axis(n.dodge = 2))`
  - Check out this blog post for dealing with long x-axis labels: https://www.andrewheiss.com/blog/2022/06/23/long-labels-ggplot/

```{r}
phd_field %>%
  filter(broad_field != "Other") %>%
  group_by(year, broad_field) %>%
  summarize(n = sum(n_phds, na.rm=TRUE)) %>%
  ggplot(aes(x=as.factor(year), y=n, color=broad_field,
             group=broad_field))+
  geom_line()+
  gghighlight(use_direct_label=FALSE)+
  facet_wrap(~broad_field, nrow=2)+
  viridis::scale_color_viridis(discrete = TRUE, option = "H")+
  labs(title="Number of PhD Graduates per Year by Broad Field",
       caption="Data from the NSF",
       x=NULL, y=NULL)+
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 0),
        strip.background = element_blank(),
        strip.text = element_text(face="bold"),
        panel.background = element_rect(fill="white"))
```


