---
title: "Highlighter"
author: "Student"
date: '2023-02-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# The Data

```{r}
phd_field <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-02-19/phd_by_field.csv")
```

The data comes from the Survey of Earned Doctorates and is provided via [a #TidyTuesday repo](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-02-19).

### Explore the data set

```{r}

```


# Chart 1 - A single line

Make a *simple* line chart of total number of PhD graduates per year

```{r}

```


# Chart 2 - Area Under the Line

Change this line chart so that the line is slightly thicker and there is a "cyan4" shaded area under the line. Set the limits to 1000 under the min and over max of the data

```{r}

```

# Chart 3 - One Line Per Group

Make a line chart like above, however, there should be one line per `broad_field`. Drop the "Other" category. There should be 6 categories total.

```{r}

```

# Chart 4 - Labelled Lines

Let's use `gghighlight` to label each line. Simply add `gghighlight()` to the end of the code you wrote above. The default option is kind of ugly. You can alter the `label_params` following examples from [here](https://ggrepel.slowkow.com/articles/examples.html) OR you can try different label styles as listed under `line_label_type` [here ](https://yutannihilation.github.io/gghighlight/reference/gghighlight.html)

```{r}
library(gghighlight)


```
# Chart 5 - Facet Per Broad Field

Using the code from Chart 3 above, facet the chart so there is one line per facet. There should be 2 rows. Remove the legend. Rotate the year text by 90.

```{r}

```

# Chart 6 - Facet and Highlight

Add `gghighlight` to the code from Chart 5 and remove the text labels.

```{r}

```

# Final Plot

Awesome! You are now a **highlighter**.

Take the code from above and give it a makeover:
- Change the line colors
- Add a title and other labels
- Remove the strip background and make the panel titles bold
- Change the panel background to white.
- Try unrotating the years and see if you like `scale_x_discrete(guide = guide_axis(n.dodge = 2))`

```{r}

```


