---
title: "Maps Assignment"
author: "Awesome Student"
date: '2023-04-05'
output: html_document
---

# U.S. Census

- The United States Constitution mandates in Article I, Sections 2 and 9 that a complete enumeration of the US population be taken every 10 years.
- The government agency tasked with completing the enumeration of the United States population is the United States Census Bureau, part of the US Department of Commerce.
- The first US Census was conducted in 1790, with enumerations taking place every 10 years since then.

# American Community Survey

- The Census long form asks about a wider range of demographic questions on income, education, language, housing, and more. 
- The Census long form has since been replaced by the American Community Survey, which is now the premier source of detailed demographic information about the US population.

# tidycensus

"The tidycensus package, first released in 2017, is an R package designed to facilitate the process of acquiring and working with US Census Bureau population data in the R environment."

- See documentation: <https://walker-data.com/tidycensus/>.
- Read the book: [Analyzing US Census Data: Methods, Maps, and Models in R](https://walker-data.com/census-r/index.html).

With tidycensus, R users can request geometry along with attributes for their Census data, helping facilitate mapping and spatial analysis. 

## 1. Get started with tidycensus (5 points)

- Install the tidycensus package,
- Obtain a Census API key at <https://api.census.gov/data/key_signup.html>,
  - **BE SURE TO KEEP THIS SECRET!**
- Run `library(tidycensus)`,
- Uncomment line below and paste your key where it says YOUR KEY GOES HERE.
- Follow the instructions.

Once an API key is installed, you can obtain decennial Census or ACS data with a single function call.

```{r}
library(tidycensus)
# census_api_key("YOUR KEY GOES HERE", install = TRUE)
```

## 2. Get the population data by state from 2010

To get Census data, you can use the function `get_decennial()`. To run `get_decennial()`, you must specify a string representing:

- the requested geography
- a vector of Census variable IDs, represented by variable; or optionally a Census table ID, passed to table. 

The code below gets data on total population by state from the 2010 decennial Census:

```{r}
total_population_10 <- get_decennial(
  geography = "state", 
  variables = "P001001",
  year = 2010
)
```

Similarly, the `get_acs()` function retrieves data from the American Community Survey.

```{r}
born_in_mexico <- get_acs(
  geography = "state", 
  variables = "B05006_150",
  year = 2020
)
```

## 3. Search for a variable in tidycensus (5 points)

To make searching easier for R users, tidycensus offers the `load_variables()` function.

The function takes two required arguments:

- `year`, which takes the year or endyear of the Census dataset or ACS sample
- `dataset`, which references the dataset name
- For variables from the American Community Survey, users should specify the dataset as `acs1` for the 1-year ACS or `acs5` for the 5-year ACS

```{r}
v16 <- load_variables(2016, "acs5/profile", cache = TRUE)
```

Let's say we want to analyze the percentage of total households with a broadband Internet subscription. What variable should we use (column `name` from `v16`)?

ANSWER:

---

## 4. Finding geography and variables in tidycensus (6 points)

The geography parameter in `get_acs()` and `get_decennial()` allows users to request data aggregated to common Census enumeration units.

See table at: <https://walker-data.com/census-r/an-introduction-to-tidycensus.html#geography-and-variables-in-tidycensus>.

Today, we'll focus on the `school district (unified)` geography. For the variable from Step 3, let's find the data for Tennessee.

```{r}
pct_with_bb <-
    get_acs(
        geography = _________, # geography that we're focusing on
        variables = _______, # variable from Step 3
        state = "TN",
        geometry = TRUE
    )
```

1. What type of data is `pct_with_bb`?

ANSWER:

2. How many school districts are in Tennessee, based on this data?

ANSWER:

## 5. Mapping data

Now, let's represent the data with a choropleth map. Please do the following:

1. Specify the fill as the percentage of total households with a broadband Internet subscription
2. Add a color palette
3. Edit the theme

```{r}
ggplot(data = pct_with_bb, 
       aes(fill = _____)) + 
  geom_sf() +
  coord_sf()
```

## Bonus

Create another map using tidycensus.

## 6. Reflection

Important: After you knit, check the HTML file. 

- Does it appear as you intended?
- Does any output print that is too long?
- Do your name and date appear?

Share any questions you have in Canvas about fine-tuning your .Rmd output.

## 7. Submit

Submit for Assignment 13 in Canvas. 

**Rubric**

- Name is added: 2 points
- Section 1: 5 points
- Section 3: 5 points
- Section 4: 6 points
- Section 5: 12 points (4 each)

Total: 30 points