---
title: "My First Data Visualization"
author: "Fabulous Student"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
    warning: false
    message: false
---
<!-- First, please replace "Fabulous Student" (in the YAML header) with your name! -->

## Install Packages

Packages perform different jobs in R. Packages allow you to use specific functions in R. They allow R to do new things.

Before we can use a package, we need to install it. We can install it using `install.packages("package_name")`. We only need to run this the first time we install a package, and you typically install them in your console rather than in your R script.

For our first visualization, we are going to install (if you don't have it already):

- `tidyverse` - used for loading and wrangling data

## Load Packages

Here, please load the tidyverse package (using the library function).

```{r}

```


## Load Data

The data is located in the `week-2` folder and is called `gapminder.csv`. We will use the `read_csv` function from the `tidyverse` package to load the data.

Please replace XXX with the name gapminder_data, as we will be using that in the next code chunk

```{r}
XXX <- read_csv("gapminder.csv")
```

## Prepare Data

Below, edit `filter()` to only select the year 2007. After modifying and running this cell, make sure gapminder_cleaned only contains data from 2007.

```{r clean_data, message=FALSE, warning=FALSE}
gapminder_cleaned <- gapminder_data %>% 
  # select only the year 2007
  filter(XXXX) %>%
  # change columns
  mutate(
    # Place any country in Oceania in Asia
    continent = ifelse(continent == "Oceania", "Asia", as.character(continent)),
    # Create the factor order for the continents
    continent = factor(continent, levels=c("Asia", "Americas", "Europe", "Africa"))
  ) 
```

**OPEN RESPONSE:** How did you check that `gapminder_cleaned` only contained data from 2007? That is, how did you check that your `filter()` statement was working correctly?

RESPONSE:

## Build a Visualization

*Note:* Visualization based on example from https://ggplot2tutor.com/tutorials/gapminder

Run this cell. It will create a visualization of life expectancy and income in 2007.

```{r fig.height = 6, fig.width=10}
ggplot(data = gapminder_cleaned, 
       aes(x = gdpPercap, 
           y = lifeExp)) +
      annotate("text", x = 4000, y = 45, hjust = 0.5,
           size = 85, color = "grey80",
           label = "2007", alpha = .3)+
  geom_point(aes(size = pop, fill = continent),
             shape = 21,
             color = "black")+
  guides(size = "none",
         fill = guide_legend(override.aes = list(size = 5)))+
  scale_fill_manual(values = c("Asia" = "#c15dcb",
                                "Americas" = "#057575",
                                "Africa" = "#ff7500" ,
                                "Europe" = "#1E90FF"),
                     name=NULL) +
  scale_x_log10(breaks = c(0500, 1000, 2000, 4000,
                           8000, 16000, 32000, 64000))+
  scale_y_continuous(breaks = seq(0, 120, by = 10))+
  scale_size_continuous(range = c(1, 30))+
  annotate("curve", x = 2500, xend = 2014, y = 39, yend = 46.9, 
           color = "#606F7B", linetype = 2, size = .2,  curvature = 0.5)+
  annotate("text", x = 2300, y = 30, hjust = 0,
           size = 3.5,
           label = paste0("Nigeria had a life expectancy of\n",
                          "46.9 years and an annual income of",
                          "\n$2014 per year per person in 2007"))+
    labs(
    x = "Income",
    y = "Life expectancy",
    title = "Life Expectancy and Income in 2007",
    subtitle = paste0("In the following visualization you can see the relationship between income and life expectancy among all countries in 2007.",
                      "\nAfrican countries are still lagging behind in terms of general life expectancy. The European and American countries",
                      "\nare the healthiest and richest countries in the world."),
    caption = "per person (GDP/capita, PPP$ inflation-adjusted)"
  ) +
  theme(
    panel.background =element_rect(fill="white", color="white"), 
    plot.margin = unit(rep(1, 4), "cm"),
    plot.title = element_text(size=14, face="bold"),
    plot.caption = element_text(size=8, color="grey50"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(size = 0.2, 
                                    color = "#e5e5e5"),
    axis.title.y = element_text(margin = margin(r = 15), 
                                size = 11),
    axis.title.x = element_text(margin = margin(t = 15), 
                                size = 11),
    axis.line = element_line(color = "#999999", 
                             size = 0.2),
    legend.position = "top"
  ) +
  coord_cartesian(ylim = c(0, 100))
```

After successfully buliding the plot, change **one thing** in the code and re-run it. It could be something like changing a color, or clarifying the title or axis label(s).

**OPEN RESPONSE:** What one thing did you change?

RESPONSE: 

## Save the plot

```{r}
ggsave(plot=last_plot(), filename = "gapminder.jpg", height = 6, width=10)
```

## Rubric

|                     | Points Possible | Points Earned |
|---------------------|-----------------|---------------|
| File knits to HTML  | 10              |               |
|All responses correct.  | 10              |               |
| .html is submitted. | 5               |               |
| .jpg is submitted   | 5               |               |


## Render and Submit

Complete the following steps to render and publish your work:

1.  First, double-check check that the the name of the `author:` in the [YAML header](https://bookdown.org/yihui/rmarkdown-cookbook/rmarkdown-anatomy.html#yaml-metadata) at the very top of this document displays your name. The YAML header controls the style and feel for rendered document but doesn't actually display in the final output.

2.  Next, click the Preview button in the toolbar above to "render" your Quarto document to a [HTML](https://bookdown.org/yihui/rmarkdown/html-document.html) file that will be saved in your week-2 folder. You should see a formatted webpage appear in your Viewer tab in the secondary sidebar or in a new browser window. Let me know if you run into any issues with rendering! 

3. Upload the HTML file that is now present in the same folder as this Quarto file to Canvas to receive credit! Also, please upload the JPG file to receive full credit (so, you will upload TWO files for this assignment).
