---
title: "Mini Project 1"
author: "Amazing Student"
date: '2022-12-23'
output: html_document
---

# Assignment Introduction

Explore the U.S. News and World Report ranking data using the data created by Reiter. 

Please briefly read about the *National University Rankings* Excel data set here:
https://andyreiter.com/datasets/

The three sections you must complete are as follows:

1. *Explore*: Demonstrate different ways to explore a data set and become familiar with its contents.

2. *Summarize*: Use various `dplyr` functions to filter, condense, aggregate, and transform the data set into various objects that can be used for visualization

3. *Visualize*: Present simple but useful visualizations that depict interesting information in an aesthetically appealing way.

This is quite open-ended; there are many different sheets (individual files) within the Excel workbook. Which you use is up to you. Code to prepare the 2020 (the last sheet) and national rankings (the first) are provided in this week's module.

# Explore

Here, load and then explore using non-data visualization means. How many rows and columns are there? What do you notice about the data - what is present and what is missing? Add 3-5 bullet pointed notes below one or more code chunks for this step.

# Summarize

Once you are familiar with the data, think of two questions you think the data can answer. Write the questions below and *then* use summarize (and other code) to just begin to explore them. Note: you will build upon the summaries in the Visualization section. Note, this doesn't have to be very fleshed out or rigorous: this is about narrowing your exploration in light of questions you could ask of the data.

Question 1: 

```{r}

```

Question 2: 

```{r}

```

# Visualize

Keeping in mind all of the principles of visualization we have learned, all of the `ggplot` functions we have practiced, and all of the visualization code you have seen, develop a visualization that uses the data above. Each visualization should:

1. Present the information clearly
2. Use a custom or non-default color palette
3. Use `theme_minimal` or another theme
4. Have a title, using `ggtitle("title here")`

Visualization 1

```{r}

```

Visualization 2

```{r}

```

## Reflection

Please add a few sentences reflecting on what went well and what was a challenge.

## Knit and submit

Be sure to add your name and date. This time, please change the title to something of your choosing that you think captures the work you have done.

Please submit your work as an HTML file in Canvas for Mini Project 1! Good work!

## Grading Criteria

| Criteria                                                            | Yes/No |
|:--------------------------------------------------------------------|:-------|
| The file knits without errors                                       |   []   |
| Functions to explore the data are used correctly                    |   []   |
| The data summarization answers each question the student asks       |   []   |
| The information each visualization depicts is clear                 |   []   |
| Each visualization employees proper color principles                |   []   |
|                                                                     |   []   |
