---
title: "Assignment 6"
output: html_document
author: ""
date: ""
---

# Loading, setting up

Please add your name and the data above

# Points

```{r}

```

# Histograms

For this assignment, we are going to look at tuition and fees by college/university for 2018-2019, along with school type, degree length, state, in-state vs out-of-state from the [Chronicle of Higher Education](https://www.chronicle.com/interactives/tuition-and-fees.

```{r}


```

## Become Familiar with the Data

As with any data set, your first step is to become familiar with the variables, values, and structure of the data:

```{r}

```


## Building Distributions

### What does the distribution of in-state tuition look like across all states and college/university types? Make a simple histogram, simple boxplot, and density plot -- one in each of the three code chunks below.

```{r}

```


```{r}

```

```{r}

```

Write a sentence or two to describe your findings:


### How does the distribution of in-state tuition vary by college/university types? 

Use `ggplot` to make a histogram. Use `fill` and a facet (faceting the same variable you `fill` on.

```{r}

```

Now, use `ggplot` to make a density plot, setting `fill` and `alpha` (like in today's slides).

```{r}

```

Now, use `ggplot` to make a violin plot.

```{r}

```

Write a sentence or two to describe your findings, noting which of the three graphs you created you think is _most_ effective and why.


What do you notice about this plot? Write a sentence or two to summarize a take-away:



## Knit and submit as HTML

Vóila!
